---
title: "UPAS Analysis"
output:
  html_document:
    toc: true
    toc_float: true
    theme: paper
---

```{r global_options, include=FALSE}
knitr::opts_chunk$set(fig.path = 'figures/',
  warning = FALSE,
  message = FALSE,
  echo = FALSE,
  fig.width = 10, fig.height = 3,
  cache = FALSE)
```

```{r}
source("../functions_epic.R")
```

---

# Read Metadata

```{r}
grav_meta <- read_sheet("18_J7ZQgnuji-r6ovpTjmlvdz3xUGBYzy0u_ACadLG-c",
                        sheet = "metadata")

meta <- read_rds("../drive_sync/epic_homes/r_epic_homes/output/upas/upas_summary.rds")

upas_log <- read_sheet("1PnPjgbYWljb5oXoSCBqpJb2pi7gU0Kzre5lx4H-3i70",
                       sheet = "upas", col_types = "c")
```

---

# Gravimetric

* Read Data

```{r}
grav <- read_sheet("18_J7ZQgnuji-r6ovpTjmlvdz3xUGBYzy0u_ACadLG-c",
                   sheet = "data", col_types = "c") %>%
  filter(date > as.Date("2021-01-01")) %>%
  mutate(id_filter = str_pad(id_filter, 4, "left", "0"),
         id_keeper = str_pad(id_keeper, 4, "left", "0"))
```

* Organize Data

```{r}
pm25 <- grav %>%
  mutate(date = as.Date(date, format = "%Y-%m-%d")) %>%
  left_join(upas_log %>% select(id_filter, id_home, visit, location),
            by = "id_filter") %>%
  left_join(meta %>% select(id_home, visit, location,
                            volume, duration,
                            start, end),
            by = c("id_home", "visit", "location")) %>%
  mutate_at(vars("mass", "volume", "duration"), as.numeric)
```

* Check for transcription errors

```{r}
delta <- pm25 %>%
  group_by(id_filter, type) %>%
  summarise(delta = max(mass, na.rm = TRUE) - min(mass, na.rm = TRUE),
            .groups = "drop") %>%
  filter(delta > 0.05) # difference greater than 0.05 mg
```

Note there are `r nrow(delta)` replicate measurements with a difference in mass above 0.05 mg. 


## PM2.5

* Calculate PM2.5 concentration

```{r}
pm25 <- pm25 %>%
  group_by(id_home, visit, location, type, volume, duration, start, end) %>%
  summarise(mass = mean(mass, na.rm = TRUE), .groups = "drop") %>%
  pivot_wider(names_from = "type", values_from = "mass") %>%
  mutate(d_mass = post - pre,
         conc = (d_mass * 1000) / (volume / 1000)) %>%
  mutate(conc = if_else(duration < 24, NA_real_, conc)) # samples must be longer than 24 hours
```

* Plot PM2.5 concentration

```{r}
ggplot(pm25 %>% filter(!grepl("blank", location))) +
  geom_boxplot(aes(x = location, y = conc)) +
  theme_bw() +
  xlab("") + ylab("PM2.5 Concentration (ug/m^3)") +
  ggtitle("Samples") +
  scale_y_log10()
```

* impute blank concentration equivalent

```{r}
blanks <- pm25 %>% 
  filter(location == "blank") %>%
  mutate(conc = (d_mass * 1000) / ((24*7*60*2)/1000)) # seven day sample
```

* blank equivalent concentration

```{r, fig.width=5}
ggplot(blanks, aes(y = conc)) +
  geom_boxplot() +
  theme_bw() +
  xlab("") + ylab("PM2.5 Concentration (ug/m^3)") +
  ggtitle("Blanks")
```

```{r}
lod <- sd(blanks$conc, na.rm = TRUE) * 3
```

The LOD is currently `r round(lod, 3)` micrograms per cubic meter.

* Sample duration

```{r}
ggplot(meta, aes(x = as.numeric(duration) /24 )) +
  geom_histogram(bins = 7, fill = "grey80", color = "blue") +
  theme_bw() +
  xlab("Days") +
  ggtitle("Sample duration")
```

## Compare to OMNI

* Sample Info

```{r}
data <- pm25 %>%
  filter(!grepl("blank", location)) %>%
  na.omit() %>%
  mutate(pattern = paste("^omni.*", id_home, location, sep = "_"),
         files = map2("../drive_sync/epic_homes/r_epic_homes/output/omni", pattern, list.files, full.names = TRUE),
         start_ = as.Date(start) - 1,
         end_ = as.Date(end) + 1,
         dates = map2(start_, end_, seq.Date, by = "day"),
         dates = map(dates, paste, collapse = "|"),
         files = map2(dates, files, grep, value = TRUE)) %>%
  select(-start_, -end_) %>%
  mutate(omni = map(files, read_omni_rds_files))
```

```{r}
out <- data %>%
  filter(lengths(files) > 0) %>%
  mutate(pm25_omni = pmap(list(start, end, omni), pm25_mean)) %>%
  mutate(pm25_all = map(.x = omni, .f = ~mean(.x$pm25, na.rm = TRUE))) %>%
  unnest(pm25_omni) %>%
  select(-omni) %>% 
  mutate(diff = ((conc - pm25_omni)^2)^0.5,
         g = if_else(diff > 3, TRUE, FALSE))
```

```{r}
out %>% group_by(g) %>% count()
```


```{r fig_omni_vs_filter, fig.width=4.5, fig.height=4.5}
ggplot(out, aes(x = conc, y = pm25_omni, color = location)) +
  geom_point() +
  #geom_smooth(method = "lm", formula = "y ~ x", se = FALSE) +
  theme_bw() +
  geom_abline(slope = 1, intercept = 0) +
  ylim(0,NA) + xlim(0,NA) +
  ylab("OMNI (ug/m^3)") + xlab("Filter (ug/m^3)")
```

```{r}
model <- lm("pm25_omni~conc", data = out)

broom::tidy(model, conf.int = TRUE) %>%
  kable(digits = c(NA, 1, 1, 1, 6 , 1, 1), caption = "OMNI vs. Filter PM2.5") %>%
  kable_paper(bootstrap_options = "striped", full_width = F)
```



---

# Black Carbon

* read data

```{r}
files <- list.files("../drive_sync/epic_homes/data/filters/soot_scan_csv", full.names = TRUE, pattern = ".csv$")

data_bc <- map(files, read_csv, col_types = cols(.default = "c")) %>%
  bind_rows() %>%
  rename_all(clean_names) %>%
  mutate(when = sub("epic_", "", description),
         date_analyzed = as.Date(datetime, format = "%m/%d/%y")) %>%
  select(filter_id, sampleir, when, date_analyzed) %>%
  rename(id_filter = "filter_id", ir = "sampleir") %>%
  mutate(id_filter = str_pad(id_filter, 4, side = "left", pad = "0")) %>%
  mutate(ir = as.numeric(ir))
```

* organize data

```{r}
bc_dates <- data_bc %>%
  left_join(upas_log %>% select(id_home, visit, location, id_filter),
            by = "id_filter") %>%
  left_join(meta %>% select(id_home, visit, location,
                            volume, duration,
                            start, end),
            by = c("id_home", "visit", "location")) %>%
  select(id_filter, when, date_analyzed) %>%
  group_by(id_filter, when, date_analyzed) %>%
  summarise_all(first, .groups = "drop") %>%
  pivot_wider(names_from = "when", values_from = "date_analyzed") %>%
  rename(date_pre = "pre", date_post = "post")
```

* blank dates

```{r}
blank_dates <- data_bc %>%
  left_join(upas_log %>% select(id_home, visit, location, id_filter),
            by = "id_filter") %>%
  left_join(meta %>% select(id_home, visit, location,
                            volume, duration,
                            start, end),
            by = c("id_home", "visit", "location")) %>%
  filter(location == "blank") %>%
  select(id_filter, when, date_analyzed) %>%
  group_by(id_filter, when, date_analyzed) %>%
  summarise_all(first, .groups = "drop") %>%
  pivot_wider(names_from = "when", values_from = "date_analyzed") %>%
  rename(date_pre = "pre", date_post = "post")
```

* blank values

```{r}
blank_values <- data_bc %>%
  left_join(upas_log %>% select(id_home, visit, location, id_filter),
            by = "id_filter") %>%
  left_join(meta %>% select(id_home, visit, location,
                            volume, duration,
                            start, end),
            by = c("id_home", "visit", "location")) %>%
  filter(location == "blank") %>%
  select(id_filter, when, ir) %>%
  group_by(id_filter, when) %>%
  summarise(ir = mean(ir, na.rm = TRUE), .groups = "drop") %>%
  pivot_wider(names_from = "when", values_from = "ir")
```

* blank day of analysis correction

```{r}
blanks_bc <- blank_values %>%
  left_join(blank_dates, by = c("id_filter")) %>%
  mutate(delta = post - pre)
```

* change in blank ATN

Note: samples 0001 to 0100 all have the same pre-scan day

```{r}
ggplot(blanks_bc, aes(x = date_post, y = delta)) +
  geom_point() +
  theme_bw() +
  ylab("Post:Pre dAtn") +
  xlab("Date Post")
```

```{r}
blanks_bc_mean <- blanks_bc %>%
  group_by(date_pre, date_post) %>%
  summarise(blank_atn_cor = mean(delta, na.rm = TRUE), .groups = "drop")

blanks_bc_mean
```

* Calculate BC

```{r}
data_bc <- data_bc %>%
  group_by(id_filter, when) %>%
  summarise(ir = mean(ir, na.rm = TRUE), .groups = "drop") %>%
  pivot_wider(names_from = "when", values_from = "ir") %>%
  na.omit() %>%
  left_join(upas_log %>% select(id_home, visit, location, id_filter),
            by = "id_filter") %>%
  left_join(meta %>% select(id_home, visit, location,
                            volume, duration,
                            start, end),
            by = c("id_home", "visit", "location")) %>%
  mutate_at(vars("volume", "duration"), as.numeric)
```

```{r}
bc <- data_bc %>%
  left_join(bc_dates, by = c("id_filter")) %>%
  left_join(blanks_bc_mean, by = c("date_pre", "date_post")) %>%
  mutate(duration = if_else(location == "blank", 168, duration)) %>% # assume blanks run for 7 days
  filter(duration > 24) %>% # only samples that ran for > 24 hours
  mutate(bc = bc_calc(pre + blank_atn_cor, post, 2, 0.00045, duration * 60 * 60))
```

* Plot BC

```{r}
ggplot(bc %>% filter(!(location == "bedroom")), aes(x = location, y = bc)) +
  geom_boxplot() +
  theme_bw() +
  ylab("micrograms per cubic meter") +
  xlab("") +
  ggtitle("BC Mass Equivalent")
```

---

# Write Data

```{r}
# write_rds(bc, paste0("../output/bc/bc_",
# Sys.Date(),".rds"))
# # make data and backup
# write_rds(pm25, paste0("../output_2021-07-14/pm25/pm25.rds"))
# write_rds(pm25, paste0("../output_2021-07-14/pm25/pm25_",
# Sys.Date(),".rds"))

```

