---
title: "omni_hourly_correlation"
author: "Andrew Purgiel"
date: "7/22/2021"
output: html_document
---
---
title: "omni_hourly_correlation"
author: "Andrew Purgiel"
date: "1/13/2021"
output: html_document
---

```{r global_options, include=FALSE}
knitr::opts_chunk$set(fig.path = 'figures/',
  warning = FALSE,
  message = FALSE,
  echo = FALSE,
  fig.width = 10, fig.height = 3,
  cache = FALSE)
```

---

```{r libraries}
library(dplyr)
library(purrr)
library(tidyr)
library(openair)
library(ggplot2)
library(readr)
library(googlesheets4)
library(lubridate)
library(gridExtra)
```

```{r data_import}
omni_hourly <- read_rds('./csv_created/omni_hourly_calibrated.rds') %>%
  rename(datetime = datehour)

home_type_df <- read_csv('../sense/csv_created_sense/home_type_df.csv')
```

# only use data up to June 2021
```{r censor_date}
omni_hourly <- omni_hourly %>% filter(datehour<ymd_hms('2021-06-01 00:00:00'))


```


```{r define_functions}

##Define a char vector of home numbers using a number vector,
##ex: x <- home.list(c(1:15)) for homes 1-15
threedig <- function(x) {
  if (nchar(x) == 1) {a <- paste0('00', x)
  return(a)
  }
  
  if (nchar(x) == 2) {a<- paste0('0', x)
  return(a)
  }
  else return(a)
}

home.list <- function(x) sapply(x, threedig)


 # function to extract a legend from one plot for use in whole plot grid
 # reference: https://stackoverflow.com/questions/13649473/add-a-common-legend-for-combined-ggplots
 g_legend<-function(a.gplot){
    tmp <- ggplot_gtable(ggplot_build(a.gplot))
    leg <- which(sapply(tmp$grobs, function(x) x$name) == "guide-box")
    legend <- tmp$grobs[[leg]]
    return(legend)}
 
 # misc------------------------------------------------

##Define a char vector of home numbers using a number vector,
##ex: x <- home.list(c(1:15)) for homes 1-15
threedig <- function(x) {
  if (nchar(x) == 1) {a <- paste0('00', x)
  return(a)
  }
  
  if (nchar(x) == 2) {a<- paste0('0', x)
  return(a)
  }
  else return(a)
}

home.list <- function(x) sapply(x, threedig)


#function to make density plot of variable x (a column)
dens.plot <- function(data, x) {
  
ggdensity(pull(data, all_of(x)), 
          main = paste("Density plot of", x),
          xlab = x)
}



#Mean and sd functions to ignore NA values
mean_NA <- function(x, na.rm = na.rm) {
  mean(x, na.rm = TRUE)}

sd_NA <- function(x, na.rm = na.rm) {
  sd(x, na.rm = TRUE)}

#Function to only display 3 significant figures (for tables)
signif3 <- function(x){
  signif(x, digits = 3)
}



#Function found online for geometric mean to use for plots
#webpage: https://stackoverflow.com/questions/2602583/geometric-mean-is-there-a-built-in
#adjusted so zeros are not ignored, just added one, to all values and subtract at end
#adjusted "length" to ignore values that are NA


gm = function(x, na.rm=TRUE){
  if(any(x < 0, na.rm = TRUE)){
    return(NaN)
  }
  if(any(x == 0, na.rm = TRUE)){
    exp(sum(log(x+1), na.rm=na.rm) / length(x[!is.na(x)]))-1
  }
  else {
    exp(sum(log(x[x > 0]), na.rm=na.rm) / length(x[!is.na(x)]))
  }
}



#make low and high sd "interval" functions
low.sd = function(x){
  mean_NA(x)-sd_NA(x)
}

high.sd = function(x){
  mean_NA(x)+sd_NA(x)
}


#create function for standard error
std.error = function(x, na.rm=TRUE){
  sd_NA(x)/sqrt(length(x[!is.na(x)]))
}

##make low and high 95% conf interval (default 95%)
low.conf = function(x){
  gm(x)-1.96*std.error(x)
}

high.conf = function(x){
  gm(x)+1.96*std.error(x)
}



##Function to make table for plots of real time OMNI data
##averaged by hour of day, weekday, month, or a combination
time.table <- function(data, period,
                       start_date = "1900-01-13 00:00:00",
                       end_date = "9999-08-13 00:00:00",
                       groupers = NULL, # vector of variables to group by
                       # arithmetic mean if FALSE, geometric if TRUE 
                       geometric = FALSE 
                       ) {
  
  #use start and end date to define timespan during which to use data
  a <- data %>%
    filter(datetime > ymd_hms(start_date) &
             datetime < ymd_hms(end_date))
  
  #if geo is FALSE (default), use arithmetic mean and standard deviation
  #to plot line and error bars respectively
  #if geo is TRUE, use geometric mean and 95% conf interval
  #to plot line and error bars respectively
  if(geometric == FALSE){
    mean.val <- function(x) {mean_NA(x)}
    high.val <- function(x) {high.sd(x)}
    low.val <- function(x) {low.sd(x)}
  } else {
    mean.val <- function(x) {gm(x)}
    high.val <- function(x) {high.conf(x)}
    low.val <- function(x) {low.conf(x)}
  }
  
  #####average and plot values by the specified time period
  #hour of day
  if (period == 'hour'){
    a <- a %>% 
      mutate(hour = hour(datetime)) %>%
      count(hour, home) %>% # count amount of observations used for each average
      full_join(
        a %>%
          mutate(hour = hour(datetime)) %>%
      group_by(hour, .dots = groupers) %>% 
      summarize_if(is.numeric, list(mean.val = mean.val,
                                    low.val = low.val,
                                    high.val = high.val))%>%
      ungroup()) %>%
      mutate(hour = as.numeric(hour))
    
      }
  
  #weekday
  if (period == 'day'){
    a <- a %>% 
      mutate(weekday = wday(datetime, label = TRUE)) %>% 
      count(weekday, home) %>% # count amount of observations used for each average
      full_join(
        a %>%
          mutate(weekday = wday(datetime, label = TRUE)) %>% 
          
      group_by(weekday, .dots = groupers) %>% 
      summarize_if(is.numeric, list(mean.val = mean.val,
                                    low.val = low.val,
                                    high.val = high.val))%>%
      ungroup())
    
  }
  
  # #weekday and hour of each day
  # if (period == 'day.hour'){
  #   a <- a %>% 
  #     mutate(weekday = wday(datetime, label = TRUE),
  #            hour = hour(datetime)) %>%
  #     group_by(weekday, hour, .dots = groupers) %>% 
  #     summarize_if(is.numeric, list(mean.val = mean.val,
  #                                   low.val = low.val,
  #                                   high.val = high.val))%>%
  #     ungroup() %>%
  #     mutate(hour = as.numeric(hour))
  #   
  # }
  
  #month
 if (period == 'month'){
    a <- a %>% 
      mutate(month = floor_date(datetime, unit = 'month')) %>%
      count(month, home) %>% # count amount of observations used for each average
      full_join(
        a %>%
          mutate(month = floor_date(datetime, unit = 'month')) %>%
          
      group_by(month, .dots = groupers) %>% 
      summarize_if(is.numeric, list(mean.val = mean.val,
                                    low.val = low.val,
                                    high.val = high.val))%>%
      ungroup())
  }
  
  # #month and hour of each day
  # if (period == 'month.hour'){
  #   a <- a %>% 
  #     mutate(month = month(datetime, label = TRUE),
  #            hour = hour(datetime)) %>%
  #     group_by(month, hour, .dots = groupers) %>% 
  #     summarize_if(is.numeric, list(mean.val = mean.val,
  #                                   low.val = low.val,
  #                                   high.val = high.val))%>%
  #     ungroup() %>%
  #     mutate(hour = as.numeric(hour))
  #   
  # }
  
  #     if (period == 'date.day'){
  #   a <- a %>% 
  #     mutate(datetime = floor_date(datetime, unit = 'days')) %>%
  #     group_by(datetime, .dots = groupers) %>% 
  #     summarize_if(is.numeric, list(mean.val = mean.val,
  #                                   low.val = low.val,
  #                                   high.val = high.val))%>%
  #     ungroup() %>%
  #     mutate()
  # }

  return(a)

}

    # hourly simple plot-----------------------------------



    # plot without labels and such
    plot.hourly.simp <- function(dat, metric, err_ribbon = TRUE) {
      
      # define upper y-limit for plot based on metric
      y_range <- case_when(
        metric == 'pm25' ~ pm25_lim,
        metric == 'voc' ~ voc_lim,
        metric == 'co2' ~ co2_lim,
        metric == 'temp' ~ temp_lim,
        metric == 'humid' ~ humid_lim,
        metric == 'lux' ~ lux_lim,
        metric == 'spl_a' ~ spl_a_lim)
      
      ggplot(dat, aes(x = hour, y = get(paste0(metric, '_mean.val')), color = home))+
        geom_line( size = line_size)+
        ##geom_errorbar(aes(ymax = pm25_high.val, ymin = pm25_low.val))+ ##bars instead?
        geom_ribbon(aes(ymax = get(paste0(metric, '_high.val')),
                        ymin = get(paste0(metric, '_low.val')), fill = home),
                    alpha = if_else(err_ribbon == TRUE, 0.2, 0), color = NA)+
        labs(y = metric,
             x = NULL)+
        scale_x_continuous(limits = c(0,24),
                           breaks = c(0,6,12,18),
                           expand = c(0,0))+
        theme_bw()+
        coord_cartesian(ylim = y_range)+
        theme(plot.title = element_blank(),
      axis.text.y = element_blank(),
      axis.text.x = element_text(size = xsmall),
      axis.title = element_blank(),
      legend.position = 'none')+
        # make point size proportional to # of obs, with 0 obs = size 0
  geom_point(aes(size = n))+
        scale_size_area(max_size = max_point_size)
      
    }
    
    
    
    # daily simple plot-----------------------------------
    
    
    # plot without labels and such
    plot.weekday.simp <- function(dat, metric, err_ribbon = TRUE) {
      
      # define upper y-limit for plot based on metric
      y_range <- case_when(
        metric == 'pm25' ~ pm25_lim,
        metric == 'voc' ~ voc_lim,
        metric == 'co2' ~ co2_lim,
        metric == 'temp' ~ temp_lim,
        metric == 'humid' ~ humid_lim,
        metric == 'lux' ~ lux_lim,
        metric == 'spl_a' ~ spl_a_lim)
      
      ggplot(dat, aes(x = weekday, y = get(paste0(metric, '_mean.val')), color = home,
                      group = home))+ # need group to plot line for categorical variable
        geom_line( size = line_size)+
        #geom_errorbar(aes(ymax = pm25_high.val, ymin = pm25_low.val))+ ##bars instead?
        geom_ribbon(aes(ymax = get(paste0(metric, '_high.val')),
                        ymin = get(paste0(metric, '_low.val')), fill = home),
                    alpha = if_else(err_ribbon == TRUE, 0.2, 0), color = NA)+
        labs(y = metric,
             x = NULL)+
        
        theme_bw()+
        coord_cartesian(ylim = y_range)+
        theme(plot.title = element_blank(),
              axis.text.y = element_blank(),
              axis.text.x = element_text(size = xsmall),
              axis.title = element_blank(),
              legend.position = 'none')+
        # make point size proportional to # of obs, with 0 obs = size 0
        geom_point(aes(size = n))+
        scale_size_area(max_size = max_point_size)
    }
    
    

    
    # monthly simple plot-----------------------------------
    
    

    # plot without labels and such
    plot.monthly.simp <- function(dat, metric, err_ribbon = TRUE) {
      
      # define upper y-limit for plot based on metric
      y_range <- case_when(
        metric == 'pm25' ~ pm25_lim,
        metric == 'voc' ~ voc_lim,
        metric == 'co2' ~ co2_lim,
        metric == 'temp' ~ temp_lim,
        metric == 'humid' ~ humid_lim,
        metric == 'lux' ~ lux_lim,
        metric == 'spl_a' ~ spl_a_lim)
      
      ggplot(dat, aes(x = month, y = get(paste0(metric, '_mean.val')), color = home,
                      group = home))+ # need group to plot line for categorical variable
        geom_line( size = line_size)+
        #geom_errorbar(aes(ymax = pm25_high.val, ymin = pm25_low.val))+ ##bars instead?
        geom_ribbon(aes(ymax = get(paste0(metric, '_high.val')),
                        ymin = get(paste0(metric, '_low.val')), fill = home),
                    alpha = if_else(err_ribbon == TRUE, 0.2, 0), color = NA)+
        labs(y = metric,
             x = NULL)+
        
        theme_bw()+
        coord_cartesian(ylim = y_range)+
        theme(plot.title = element_blank(),
              axis.text.y = element_blank(),
              axis.text.x = element_text(size = xsmall),
              axis.title = element_blank(),
              legend.position = 'none')+
        # make point size proportional to # of obs, with 0 obs = size 0
        geom_point(aes(size = n))+
        scale_size_area(max_size = max_point_size)
    }
    
    
    
  
# grid simple plot-----------------------------------------

##Function to make table for plots of real time OMNI data
##averaged by hour of day, weekday, month, or a combination
time.plot <- function(data, period,
                      metrics, # metrics to plot (i.e. c('pm25', 'voc'))
                       start_date = "1900-01-13 00:00:00",
                       end_date = "9999-08-13 00:00:00",
                       groupers = NULL, # vector of variables to group by
                       # arithmetic mean if FALSE, geometric if TRUE 
                       geometric = FALSE,
                      err_ribbon_plot = TRUE
                       ) {
  
  #use start and end date to define timespan during which to use data
  a <- data %>%
    filter(datetime > ymd_hms(start_date) &
             datetime < ymd_hms(end_date))
  
  #if geo is FALSE (default), use arithmetic mean and standard deviation
  #to plot line and error bars respectively
  #if geo is TRUE, use geometric mean and 95% conf interval
  #to plot line and error bars respectively
  if(geometric == FALSE){
    mean.val <- function(x) {mean_NA(x)}
    high.val <- function(x) {high.sd(x)}
    low.val <- function(x) {low.sd(x)}
  } else {
    mean.val <- function(x) {gm(x)}
    high.val <- function(x) {high.conf(x)}
    low.val <- function(x) {low.conf(x)}
  }
  
  #####average and plot values by the specified time period
  #hour of day
  if (period == 'hour'){
    a <- a %>% 
      mutate(hour = hour(datetime)) %>%
      count(hour, home) %>% # count amount of observations used for each average
      full_join(
        a %>%
          mutate(hour = hour(datetime)) %>%
      group_by(hour, .dots = groupers) %>% 
      summarize_if(is.numeric, list(mean.val = mean.val,
                                    low.val = low.val,
                                    high.val = high.val))%>%
      ungroup()) %>%
      mutate(hour = as.numeric(hour))
    
    
    a <- lapply(metrics, plot.hourly.simp, dat = a, err_ribbon = err_ribbon_plot)
    
          a<- do.call('grid.arrange', c(a, ncol = 1))

  }
  
  #weekday
  if (period == 'day'){
    a <- a %>% 
      mutate(weekday = wday(datetime, label = TRUE)) %>% 
      count(weekday, home) %>% # count amount of observations used for each average
      full_join(
        a %>%
          mutate(weekday = wday(datetime, label = TRUE)) %>% 
          
      group_by(weekday, .dots = groupers) %>% 
      summarize_if(is.numeric, list(mean.val = mean.val,
                                    low.val = low.val,
                                    high.val = high.val))%>%
      ungroup())
    
    
    
    a <- lapply(metrics, plot.weekday.simp, dat = a, err_ribbon = err_ribbon_plot)
    
              a<- do.call('grid.arrange', c(a, ncol = 1))


  }
  
  
  #month
  if (period == 'month'){
    a <- a %>% 
      mutate(month = month(datetime, label = TRUE)) %>%
      count(month, home) %>% # count amount of observations used for each average
      full_join(
        a %>%
          mutate(month = month(datetime, label = TRUE)) %>%
          
      group_by(month, .dots = groupers) %>% 
      summarize_if(is.numeric, list(mean.val = mean.val,
                                    low.val = low.val,
                                    high.val = high.val))%>%
      ungroup())
    
    
    a <- lapply(metrics, plot.monthly.simp, dat = a, err_ribbon = err_ribbon_plot)
    
              a<- do.call('grid.arrange', c(a, ncol = 1))

  }
  

  return(a)

  }


 
 

```



```{r define_variables}

##For plot labeling pruposes
xsmall <- 6
small <- 15
medium <- 20
large <- 26
line_size <- 0.5
max_point_size <- 1.5

# define y-limits for metrics (for time series plots)
pm25_lim <- c(0,60)
voc_lim <- c(0,1500)
co2_lim <- c(0,2500)
temp_lim <- c(0,25)
humid_lim <- c(0,60)
lux_lim <- c(0,1000)
spl_a_lim <- c(40,70)

# define y-limits for metrics (for difference of means plots)
pm25_diff_lim <- c(-10,10)
voc_diff_lim <- c(-400,700)
co2_diff_lim <- c(-600,1000)
temp_diff_lim <- c(-5,3.5)
humid_diff_lim <- c(-9,9)
lux_diff_lim <- c(-500,750)
pm25_diff_lim <- c(-10,10)
spl_a_diff_lim <- c(-9,9)

## for zoom:
#   pm25_lim <- c(0,40)
# voc_lim <- c(0,1000)
# co2_lim <- c(0,1500)
# temp_lim <- c(15,25)
# humid_lim <- c(20,60)
# lux_lim <- c(0,500)
# spl_a_lim <- c(40,70)




homes_all <- home.list(c(1:16))
homes_no5 <- home.list(c(1:4, 6:16))
homes_tier1 <- home_type_df %>% filter(home_type == 'tier1') %>% pull(home)
homes_tier2 <- home_type_df %>% filter(home_type == 'tier2') %>% pull(home)
homes_tier3 <- home_type_df %>% filter(home_type == 'tier3') %>% pull(home)

metrics_all <- c('pm25', 'voc', 'co2', 'temp','humid', 'lux', 'spl_a')
locations_indoor <- c('living', 'bedroom', 'kitchen')

periods_all <- c('hour', 'day', 'month')

living_data <- omni_hourly %>% filter(location == 'living')
kitchen_data <- omni_hourly %>% filter(location == 'kitchen')
bedroom_data <- omni_hourly %>% filter(location == 'bedroom')
outdoor_data <- omni_hourly %>% filter(location == 'outdoor')
garage_data <- omni_hourly %>% filter(location == 'garage')


# color blind pallette
# check http://www.cookbook-r.com/Graphs/Colors_(ggplot2)/#a-colorblind-friendly-palette
cbbPalette <- c('black' = "#000000",
                'light_orange' = "#E69F00",
                'light_blue' = "#56B4E9",
                'green' = "#009E73",
                'yellow' = "#F0E442",
                'dark_blue' = "#0072B2",
                'dark_orange' = "#D55E00",
                'purple' = "#CC79A7"
                )
# define colors for room-comparisons
room_colors <- c(cbbPalette['green'],
                   cbbPalette['purple'],
                   cbbPalette['light_orange']
                   )%>% unname()

room_breaks <- locations_indoor

```


```{r grid_pdfs, eval = FALSE}

hour.day.month.grid <- function(location, err_ribbon_plot1 = TRUE,
                                note = NULL,
                                start_date1 = "1900-01-13 00:00:00",
                       end_date1 = "9999-08-13 00:00:00") {
    a <- lapply(periods_all, time.plot,
                data = get(paste0(location, '_data')), metrics = metrics_all,
                groupers = c('home'),
                err_ribbon_plot = err_ribbon_plot1,
                start_date = start_date1,
                       end_date = end_date1)
    
    a <- do.call('grid.arrange', c(a, ncol = 3,
                                   top = paste(location, start_date1,
                                               end_date1, note, sep = '_'))) 
    
    # change name of file if not using error ribbon
            # add note to file name if specified

    file_name <- if_else(
      err_ribbon_plot1 == TRUE,
      paste0('grid_', location, '_', Sys.Date(), '_', note, '.pdf'),
      paste0('grid_', location, '_noribbon_', Sys.Date(), '_', note, '.pdf'))
    
    
    # save file as pdf
      ggsave(file_name,
           plot = a , width = 8, height = 10.5, units = 'in')
      
}

rm <- 'living'
version <- 'all time'
# test for all monitoring period
hour.day.month.grid(rm, err_ribbon_plot1 = TRUE, note = version)


season <- c('2020-9-22 00:00:00','2020-12-21 23:59:00')
season_start <- season[1]
season_end <- season[2]


version <- 'fall'
  
rm <- 'living'
# hour.day.month.grid(rm)
hour.day.month.grid(rm, err_ribbon_plot1 = FALSE, note = version,
                    start_date1 = season_start, end_date1 = season_end)

rm <- 'kitchen'
# hour.day.month.grid(rm)
hour.day.month.grid(rm, err_ribbon_plot1 = FALSE, note = version,
                    start_date1 = season_start, end_date1 = season_end)

rm <- 'bedroom'
# hour.day.month.grid(rm)
hour.day.month.grid(rm, err_ribbon_plot1 = FALSE, note = version,
                    start_date1 = season_start, end_date1 = season_end)

rm <- 'outdoor'
# hour.day.month.grid(rm)
hour.day.month.grid(rm, err_ribbon_plot1 = FALSE, note= version, 
                    start_date1 = season_start, end_date1 = season_end)

rm <- 'garage'
# hour.day.month.grid(rm)
hour.day.month.grid(rm, err_ribbon_plot1 = FALSE, note = version,
                    start_date1 = season_start, end_date1 = season_end)


```

## Note: all plots use averaged hourly data to calculate means and confidence intervals  


# Hourly 

## Overall

```{r hourly_overall, eval = FALSE}



{
  a <- time.table(omni_hourly, 'hour', groupers = 'location')
  
##PM2.5


   plotpm <- ggplot(a, aes(x = hour, y = pm25_mean.val))+
    geom_line( size = 1)+
    facet_wrap(~location)+
    ##geom_errorbar(aes(ymax = pm25_high.val, ymin = pm25_low.val))+ ##bars instead?
    geom_ribbon(aes(ymax = pm25_high.val, ymin = pm25_low.val),
                alpha = 0.2, color = NA, fill = 'orange')+
    labs(y = expression('PM'["2.5"]*'(ug/m'^3*')'),
         x = "Time",
         title = paste("PM in Homes"))+
    scale_x_continuous(limits = c(0,24),
                       breaks = c(0,6,12,18),
                       labels = c('12am', '6am','noon', '6pm'),
                       expand = c(0,0))+
    theme_bw()+
    coord_cartesian(ylim = c(0, 60))+
    theme(plot.title = element_text(hjust = 0.5),
          title = element_text(size = medium),
          axis.text = element_text(size = small),
          strip.text = element_text( size = medium),
          axis.title = element_text(size = medium))+
    geom_point(size = 2)+
          ##for extra space between facets
    theme(panel.spacing = unit(1, "lines"),
          strip.background =element_blank())

##VOC

   plotvoc <- ggplot(a, aes(x = hour, y = voc_mean.val))+
    geom_line(size = 1)+
    facet_wrap(~location)+
    ##geom_errorbar(aes(ymax = pm25_high.val, ymin = pm25_low.val))+ ##bars instead?
    geom_ribbon(aes(ymax = voc_high.val, ymin = voc_low.val),
                alpha = 0.2, color = NA, fill = 'orange')+
    labs(y = 'TVOC (ppb)',
         x = "Time",
         title = paste("TVOCs in Homes"))+
    scale_x_continuous(limits = c(0,24),
                       breaks = c(0,6,12,18),
                       labels = c('12am', '6am','noon', '6pm'),
                       expand = c(0,0))+
    coord_cartesian(ylim = c(0, 1200))+
    theme_bw()+
    theme(plot.title = element_text(hjust = 0.5),
          title = element_text(size = medium),
          axis.text = element_text(size = small),
          strip.text = element_text( size = medium),
          axis.title = element_text(size = medium))+
    geom_point(size = 2)+
     ##for extra space between facets
    theme(panel.spacing = unit(1, "lines"),
          strip.background =element_blank())
  
}
plotpm
plotvoc


```

## By Home

```{r hourly_homes, eval = FALSE, fig.height=2.5, fig.width = 12}

   # plot with details
      plot.hourly <- function(metric, data, location = NULL) {
     
              # define upper y-limit for plot based on metric
      y_range <- case_when(
        metric == 'pm25' ~ pm25_lim,
        metric == 'voc' ~ voc_lim,
        metric == 'co2' ~ co2_lim,
        metric == 'temp' ~ temp_lim,
        metric == 'humid' ~ humid_lim,
        metric == 'lux' ~ lux_lim,
        metric == 'spl_a' ~ spl_a_lim)
      
        #     y_label <- case_when(
        # metric == 'pm25' ~ expression('PM'[2.5]*', ppb'),
        # metric == 'voc' ~ 'TVOC, ppb',
        # metric == 'co2' ~ expression('CO'[2]*', ppb'),
        # metric == 'temp' ~ 'Temperature, deg C',
        # metric == 'humid' ~ 'Relative Humidity, %',
        # metric == 'lux' ~ 'Light, lx',
        # metric == 'spl_a' ~ 'Noise, dB')
      
     ggplot(data, aes(x = hour, y = get(paste0(metric, '_mean.val')), color = home))+
    geom_line( size = 1)+
    {if( is.null(location) | length(location) > 1) 
      facet_wrap(~factor(location, levels = c('living', 'kitchen', 'bedroom',
                                              'garage', 'outdoor')),
                 ncol = 5)}+
    ##geom_errorbar(aes(ymax = pm25_high.val, ymin = pm25_low.val))+ ##bars instead?
    # geom_ribbon(aes(ymax = get(paste0(metric, '_high.val')),
    #                 ymin = get(paste0(metric, '_low.val')), fill = home),
    #             alpha = 0.2, color = NA)+
    labs(y = paste('Average', metric),
         x = "Hour of Day",
         title = 'Hourly')+
    scale_x_continuous(limits = c(0,24),
                       breaks = c(0,6,12,18),
                       labels = c('12am', '6am','noon', '6pm'),
                       expand = c(0,0))+
       scale_color_discrete(name = 'Home',
                            guide = 'none'
                            )+
    theme_bw()+
    theme(plot.title = element_blank(),
          title = element_text(size = medium),
          axis.text.y = element_text(size = small),
          axis.text.x = element_text(size = small-3),
          strip.text = element_text( size = medium),
          axis.title = element_text(size = medium),
          legend.title = element_text(size = medium-3),
          panel.spacing.x = unit(1, 'lines') # add horiz space between facets
          )+
               coord_cartesian(ylim = y_range)+
        # make point size proportional to # of obs, with 0 obs = size 0
        # geom_point(aes(size = n))+
        scale_size_area(max_size = max_point_size, guide = 'none')+
       # guides(col = guide_legend(ncol = 2))+ #split up legend
          ##for extra space between facets
    theme(
          strip.background =element_blank())
      }

a <- time.table(omni_hourly, 'hour', groupers = c('home','location'))%>%
  filter(home %in% homes_no5)

plot.hourly('pm25', data = a)
plot.hourly('voc', data = a)
plot.hourly('co2', data = a)
plot.hourly('temp', data = a)




```

## By Season
* NOTE: Group 1 Homes and unclassified days omitted from data set
### Heating
```{r, fig.height=2.5, fig.width = 12}

a <- time.table(omni_hourly %>% filter(energy_cluster == 'heat'),
                'hour', groupers = c('home','location'))%>%
  filter(home %in% c(homes_tier2, homes_tier3))

plot.hourly('pm25', data = a)
plot.hourly('voc', data = a)
plot.hourly('co2', data = a)
plot.hourly('temp', data = a)
```

### Shoulder
```{r, fig.height=2.5, fig.width = 12}

a <- time.table(omni_hourly %>% filter(energy_cluster == 'shoulder'),
                'hour', groupers = c('home','location'))%>%
  filter(home %in% c(homes_tier2, homes_tier3))

plot.hourly('pm25', data = a)
plot.hourly('voc', data = a)
plot.hourly('co2', data = a)
plot.hourly('temp', data = a)
```


### AC
```{r, fig.height=2.5, fig.width = 12}

a <- time.table(omni_hourly %>% filter(energy_cluster == 'ac'),
                'hour', groupers = c('home','location'))%>%
  filter(home %in% c(homes_tier2, homes_tier3))

plot.hourly('pm25', data = a)
plot.hourly('voc', data = a)
plot.hourly('co2', data = a)
plot.hourly('temp', data = a)
```
# Daily

```{r date_day, eval = FALSE}



{A <- time.table(omni_hourly, 'date.day', groupers = 'location')
  
##PM2.5


   plotpm <- ggplot(A, aes(x = datetime, y = pm25_mean.val))+
    geom_line( size = 1)+
    ##geom_errorbar(aes(ymax = pm25_high.val, ymin = pm25_low.val))+ ##bars instead?
    geom_ribbon(aes(ymax = pm25_high.val, ymin = pm25_low.val),
                alpha = 0.2, color = NA, fill = 'orange')+
    labs(y = expression('PM'["2.5"]*'(ug/m'^3*')'),
         x = "Date",
         title = paste("PM - Average of Daily Values for all Homes"))+
    theme_bw()+
    coord_cartesian(ylim = c(0, 60))+
    theme(plot.title = element_text(hjust = 0.5),
          title = element_text(size = small),
          axis.text = element_text(size = medium),
          strip.text = element_text( size = large),
          axis.title = element_text(size = large))+
    geom_point(size = 1)+
         facet_wrap(~location)+
          ##for extra space between facets
    theme(panel.spacing = unit(1, "lines"),
          strip.background =element_blank())

##VOC

   plotvoc <- ggplot(A, aes(x = datetime, y = voc_mean.val))+
    geom_line(size = 1)+
    ##geom_errorbar(aes(ymax = pm25_high.val, ymin = pm25_low.val))+ ##bars instead?
    geom_ribbon(aes(ymax = voc_high.val, ymin = voc_low.val),
                alpha = 0.2, color = NA, fill = 'orange')+
    labs(y = 'TVOC (ppb)',
         x = "Date",
         title = paste("TVOCs - Average of Daily Values for all Homes)"))+
    coord_cartesian(ylim = c(0, 1200))+
    theme_bw()+
    theme(plot.title = element_text(hjust = 0.5),
          title = element_text(size = 18),
          axis.text = element_text(size = medium),
          strip.text = element_text( size = large),
          axis.title = element_text(size = large))+
    geom_point(size = 1)+
         facet_wrap(~location)+
          ##for extra space between facets
    theme(panel.spacing = unit(1, "lines"),
          strip.background =element_blank())
  
}
plotpm
plotvoc

```


# Weekday

## By Home
```{r weekday_homes, eval = FALSE, fig.height=2.5, fig.width = 12}

   # plot with details
      plot.weekday <- function(metric, data, location = NULL) {
     
              # define upper y-limit for plot based on metric
      y_range <- case_when(
        metric == 'pm25' ~ c(0,37),
        metric == 'voc' ~ voc_lim,
        metric == 'co2' ~ c(0,1250),
        metric == 'temp' ~ temp_lim,
        metric == 'humid' ~ humid_lim,
        metric == 'lux' ~ lux_lim,
        metric == 'spl_a' ~ spl_a_lim)
      
        #     y_label <- case_when(
        # metric == 'pm25' ~ expression('PM'[2.5]*', ppb'),
        # metric == 'voc' ~ 'TVOC, ppb',
        # metric == 'co2' ~ expression('CO'[2]*', ppb'),
        # metric == 'temp' ~ 'Temperature, deg C',
        # metric == 'humid' ~ 'Relative Humidity, %',
        # metric == 'lux' ~ 'Light, lx',
        # metric == 'spl_a' ~ 'Noise, dB')
      
     ggplot(data, aes(x = weekday, y = get(paste0(metric, '_mean.val')), color = home))+
    geom_line( aes(group = home), size = 1)+
    {if( is.null(location) | length(location) > 1) 
      facet_wrap(~factor(location, levels = c('living', 'kitchen', 'bedroom',
                                              'garage', 'outdoor')),
                 ncol = 5)}+
    ##geom_errorbar(aes(ymax = pm25_high.val, ymin = pm25_low.val))+ ##bars instead?
    # geom_ribbon(aes(ymax = get(paste0(metric, '_high.val')),
    #                 ymin = get(paste0(metric, '_low.val')), fill = home),
    #             alpha = 0.2, color = NA)+
    labs(y = paste('Average', metric),
         x = "Weekday",
         title = 'Weekday')+
    scale_x_discrete(
                       labels = c('M', 'T', 'W', 'Th', 'F', 'Sa', 'Su'),
                       breaks = c('Mon', 'Tue', 'Wed', 'Thu', 'Fri', 'Sat', 'Sun')
                       )+
       scale_color_discrete(name = 'Home')+
    theme_bw()+
    theme(plot.title = element_blank(),
          title = element_text(size = medium),
          axis.text.y = element_text(size = small),
          axis.text.x = element_text(size = small-3),
          strip.text = element_text( size = medium),
          axis.title = element_text(size = medium),
          legend.title = element_text(size = medium-3),
          panel.spacing.x = unit(1, 'lines') # add horiz space between facets
          )+
               coord_cartesian(ylim = y_range)+
        # make point size proportional to # of obs, with 0 obs = size 0
        # geom_point(aes(size = n))+
        scale_size_area(max_size = max_point_size, guide = 'none')+
          ##for extra space between facets
    theme(
          strip.background =element_blank())
      }

a <- time.table(omni_hourly, 'day', groupers = c('home','location'))%>%
  filter(home %in% homes_no5)

plot.weekday('pm25', data = a)
plot.weekday('voc', data = a)
plot.weekday('co2', data = a)
plot.weekday('temp', data = a)


```



# Monthly

## one room

```{r monthly, eval = FALSE}



rms <- c('living', 'outdoor')


##### Boxplots

# PM2.5

  
metric <- 'pm25'


a <- omni_hourly %>%
  filter(location %in% rms) %>%
  mutate(month = lubridate::month(datetime, label = TRUE)) %>%
  group_by(month, location) %>%
  mutate(outlier = get(metric) > median(get(metric), na.rm = TRUE) +
           IQR(get(metric), na.rm = TRUE) * 1.5) %>%
  ungroup()


 plotpm <- ggplot(a, aes(x = month, y = get(metric)))+
    geom_boxplot(outlier.shape = NA)+ # don't plot outliers at first
    labs(y = expression('PM'["2.5"]*'(ug/m'^3*')'),
         x = "Month",
         title = paste("PM in Homes"))+
   facet_wrap(~location)+
    theme_bw()+
    coord_cartesian(ylim = c(0, 60))+
    theme(plot.title = element_text(hjust = 0.5),
          title = element_text(size = medium),
          axis.text = element_text(size = small),
          strip.text = element_text( size = medium),
          axis.title = element_text(size = medium))+
   geom_point(data = function(x) filter_(x, ~ outlier),
              position = 'jitter', size = 1) # Outliers

 
 plotpm
 
 
 
##VOC

   
 metric <- 'voc'
  
a <- hourly %>%
  filter(location %in% rms) %>%
  mutate(month = lubridate::month(datetime, label = TRUE)) %>%
  group_by(month, location) %>%
  mutate(outlier = get(metric) > median(get(metric), na.rm = TRUE) +
           IQR(get(metric), na.rm = TRUE) * 1.5) %>%
  ungroup()
 
   
   plotvoc <- ggplot(a, aes(x = month, y = get(metric)))+
    geom_boxplot(outlier.shape = NA)+ # don't plot outliers at first
    labs(y = 'TVOC (ppb)',
         x = "Month",
         title = paste("TVOCs in Homes"))+
    coord_cartesian(ylim = c(0, 1200))+
        facet_wrap(~location)+
    theme_bw()+
    theme(plot.title = element_text(hjust = 0.5),
          title = element_text(size = medium),
          axis.text = element_text(size = small),
          strip.text = element_text( size = medium),
          axis.title = element_text(size = medium))+
   geom_point(data = function(x) filter_(x, ~ outlier),
              position = 'jitter', size = 1) # Outliers  

   
   

plotvoc




```

## By Home

```{r monthly_new_method, fig.height=2.5, fig.width = 12}



      plot.monthly <- function(metric, data, location = NULL) {
     
              # define upper y-limit for plot based on metric
      y_range <- case_when(
        metric == 'pm25' ~ c(0,40),
        metric == 'voc' ~ voc_lim,
        metric == 'co2' ~ c(0,2000),
        metric == 'temp' ~ temp_lim,
        metric == 'humid' ~ humid_lim,
        metric == 'lux' ~ lux_lim,
        metric == 'spl_a' ~ spl_a_lim)
      
        #     y_label <- case_when(
        # metric == 'pm25' ~ expression('PM'[2.5]*', ppb'),
        # metric == 'voc' ~ 'TVOC, ppb',
        # metric == 'co2' ~ expression('CO'[2]*', ppb'),
        # metric == 'temp' ~ 'Temperature, deg C',
        # metric == 'humid' ~ 'Relative Humidity, %',
        # metric == 'lux' ~ 'Light, lx',
        # metric == 'spl_a' ~ 'Noise, dB')
      
     ggplot(data, aes(x = month, y = get(paste0(metric, '_mean.val')), color = home))+
    geom_line( aes(group = home), size = 1)+
    {if( is.null(location) | length(location) > 1) 
      facet_wrap(~factor(location, levels = c('living', 'kitchen', 'bedroom',
                                              'garage', 'outdoor')),
                 ncol = 5)}+
    ##geom_errorbar(aes(ymax = pm25_high.val, ymin = pm25_low.val))+ ##bars instead?
    # geom_ribbon(aes(ymax = get(paste0(metric, '_high.val')),
    #                 ymin = get(paste0(metric, '_low.val')), fill = home),
    #             alpha = 0.2, color = NA)+
    labs(y = paste('Average', metric),
         x = "Month",
         title = 'Monthly')+
       scale_x_date("Date",
                    breaks = c(seq(from=as.Date("2020-07-01"),to=as.Date("2021-07-01"),by="month")),
               labels = c(
                 sapply(month.abb[c(1:12)],
                                       substr, start = 1, stop = 1) %>% unname(),
                 'J'))+ 
       scale_color_discrete(name = 'Home')+
    theme_bw()+
    theme(plot.title = element_blank(),
          title = element_text(size = medium),
          axis.text.y = element_text(size = small),
          axis.text.x = element_text(size = small-3),
          strip.text = element_text( size = medium),
          axis.title = element_text(size = medium),
          legend.title = element_text(size = medium-3),
          panel.spacing.x = unit(1, 'lines') # add horiz space between facets
          )+
               coord_cartesian(ylim = y_range)+
        # make point size proportional to # of obs, with 0 obs = size 0
        # geom_point(aes(size = n))+
        scale_size_area(max_size = max_point_size, guide = 'none')+
          ##for extra space between facets
    theme(
          strip.background =element_blank())
      }
      
      a <- time.table(omni_hourly, 'month', groupers = c('home','location'))%>%
  filter(home %in% homes_no5) %>% mutate(month = as.Date(month))
      

plot.monthly('pm25', data = a)
plot.monthly('voc', data = a)
plot.monthly('co2', data = a)
plot.monthly('temp', data = a)     
      
```





# Comparing variation between rooms

```{r function_room_comparison}


# function to compare diurnal trends of indoor rooms
# for specified metric
room.compare <- function(metric, data = omni_hourly,
                         simple = TRUE) {
  
  # make data for plots
a <- data %>%
  select(home, location, datetime, all_of(metric)) %>%
  filter(location %in% c('living', 'kitchen', 'bedroom'))

# then find diurnal means and sd for each room
locations <- time.table(a,
                       'hour', groupers = c('home','location'))

# find overall diurnal means and sd for pooled 
avg <- time.table(a,
                       'hour', groupers = c('home'))

# join dataframes together
compare_df <- full_join(
  locations,
  avg %>% select(home, hour, overall_mean = mean.val),
  by = c('hour', 'home')) %>%
  # subtract the overall mean from each of the room mean and interval values
  mutate(mean = mean.val-overall_mean, high = high.val-overall_mean,
         low = low.val-overall_mean)

  # define plot y limits based on metric
  y_limits <- case_when(
        metric == 'pm25' ~ pm25_diff_lim,
        metric == 'voc' ~ voc_diff_lim,
        metric == 'co2' ~ co2_diff_lim,
        metric == 'temp' ~ temp_diff_lim,
        metric == 'humid' ~ humid_diff_lim,
        metric == 'lux' ~ lux_diff_lim,
        metric == 'spl_a' ~ spl_a_diff_lim)
  

  ggplot(compare_df, aes(x = hour, y = mean, color = location))+
    geom_line( size = ifelse(simple == TRUE, 1, 1))+
    labs(y = 'Room Mean - Pooled Mean',
         x = "Hour of Day",
         title = metric)+
    scale_x_continuous(limits = c(0,24),
                       breaks = c(0,6,12,18),
                       labels = c('midnight', '6am','noon', '6pm'),
                       expand = c(0,0))+
    theme_bw()+
    coord_cartesian(ylim = y_limits)+ # defined in beginngin of function
    theme(plot.title = element_text(hjust = 0.5))+
          {if(simple == TRUE) theme(
            title = element_text(size = xsmall),
          axis.text = element_text(size = xsmall+2),
          strip.text = element_text( size = xsmall+2),
          axis.title = element_text(size = xsmall+2),
          legend.text = element_text(size = xsmall+2),
          legend.title = element_text(size = xsmall+2)
          ) else theme(
            title = element_text(size = small-2),
          axis.text = element_text(size = small),
          strip.text = element_text( size = small+2),
          axis.title = element_text(size = small-1)
          )
          }+
    geom_point(size = ifelse(simple == TRUE, 1, 2))+
          ##for extra space between facets
    theme(panel.spacing = unit(1, "lines"),
          strip.background =element_blank())+
   facet_wrap(vars(home), ncol = 5)+
   geom_hline(yintercept = 0, linetype = 'dashed')+
     scale_color_manual(
       values = room_colors,
              breaks = room_breaks,
       name = 'Room')
  # use below lines if using error ribbon
   # geom_ribbon(aes(ymax = high, ymin = low, fill = location),
   #                  alpha = 0.2, color = NA)+
   #      scale_fill_manual(
   #     values = room_colors,
   #            breaks = room_breaks,
   #     name = 'Room')
    
    
    # ggsave(paste0('room_compare_',metric, '_', Sys.Date(),'.pdf'), plot = a ,
    #        width = 10.5, height = 8, units = 'in')
  
}

# # test for one metric
# room.compare('voc')



```

## For one home/metric

```{r plot_room_comparison_example, fig.height=4, fig.width = 6}
a <- omni_hourly %>% filter(home == '010')
room.compare(metric = 'pm25', data = a, simple = FALSE)
```

## FOr all homes and metrics

```{r plot_room_comparison_all, fig.height=6.5, fig.width = 10.5, results='asis'}

a <- omni_hourly %>% filter( home %in% homes_no5)

# # test for one metric
# room.compare('pm25', data = a)

# make comparison plots for all metrics
lapply(metrics_all, function(x_metric) {
  a <- room.compare(metric = x_metric, data = a)
  print(a)
  # insert page break between plots
  cat("\n\n\\pagebreak\n")
})
```


```{r old_time_monthly_func}

# old functions before modification of month


# ##Function to make table for plots of real time OMNI data
# ##averaged by hour of day, weekday, month, or a combination
# time.table <- function(data, period,
#                        start_date = "1900-01-13 00:00:00",
#                        end_date = "9999-08-13 00:00:00",
#                        groupers = NULL, # vector of variables to group by
#                        # arithmetic mean if FALSE, geometric if TRUE 
#                        geometric = FALSE 
#                        ) {
#   
#   #use start and end date to define timespan during which to use data
#   a <- data %>%
#     filter(datetime > ymd_hms(start_date) &
#              datetime < ymd_hms(end_date))
#   
#   #if geo is FALSE (default), use arithmetic mean and standard deviation
#   #to plot line and error bars respectively
#   #if geo is TRUE, use geometric mean and 95% conf interval
#   #to plot line and error bars respectively
#   if(geometric == FALSE){
#     mean.val <- function(x) {mean_NA(x)}
#     high.val <- function(x) {high.sd(x)}
#     low.val <- function(x) {low.sd(x)}
#   } else {
#     mean.val <- function(x) {gm(x)}
#     high.val <- function(x) {high.conf(x)}
#     low.val <- function(x) {low.conf(x)}
#   }
#   
#   #####average and plot values by the specified time period
#   #hour of day
#   if (period == 'hour'){
#     a <- a %>% 
#       mutate(hour = hour(datetime)) %>%
#       count(hour, home) %>% # count amount of observations used for each average
#       full_join(
#         a %>%
#           mutate(hour = hour(datetime)) %>%
#       group_by(hour, .dots = groupers) %>% 
#       summarize_if(is.numeric, list(mean.val = mean.val,
#                                     low.val = low.val,
#                                     high.val = high.val))%>%
#       ungroup()) %>%
#       mutate(hour = as.numeric(hour))
#     
#       }
#   
#   #weekday
#   if (period == 'day'){
#     a <- a %>% 
#       mutate(weekday = wday(datetime, label = TRUE)) %>% 
#       count(weekday, home) %>% # count amount of observations used for each average
#       full_join(
#         a %>%
#           mutate(weekday = wday(datetime, label = TRUE)) %>% 
#           
#       group_by(weekday, .dots = groupers) %>% 
#       summarize_if(is.numeric, list(mean.val = mean.val,
#                                     low.val = low.val,
#                                     high.val = high.val))%>%
#       ungroup())
#     
#   }
#   
#   # #weekday and hour of each day
#   # if (period == 'day.hour'){
#   #   a <- a %>% 
#   #     mutate(weekday = wday(datetime, label = TRUE),
#   #            hour = hour(datetime)) %>%
#   #     group_by(weekday, hour, .dots = groupers) %>% 
#   #     summarize_if(is.numeric, list(mean.val = mean.val,
#   #                                   low.val = low.val,
#   #                                   high.val = high.val))%>%
#   #     ungroup() %>%
#   #     mutate(hour = as.numeric(hour))
#   #   
#   # }
#   
#   #month
#  if (period == 'month'){
#     a <- a %>% 
#       mutate(month = month(datetime, label = TRUE)) %>%
#       count(month, home) %>% # count amount of observations used for each average
#       full_join(
#         a %>%
#           mutate(month = month(datetime, label = TRUE)) %>%
#           
#       group_by(month, .dots = groupers) %>% 
#       summarize_if(is.numeric, list(mean.val = mean.val,
#                                     low.val = low.val,
#                                     high.val = high.val))%>%
#       ungroup())
#   }
#   
#   # #month and hour of each day
#   # if (period == 'month.hour'){
#   #   a <- a %>% 
#   #     mutate(month = month(datetime, label = TRUE),
#   #            hour = hour(datetime)) %>%
#   #     group_by(month, hour, .dots = groupers) %>% 
#   #     summarize_if(is.numeric, list(mean.val = mean.val,
#   #                                   low.val = low.val,
#   #                                   high.val = high.val))%>%
#   #     ungroup() %>%
#   #     mutate(hour = as.numeric(hour))
#   #   
#   # }
#   
#   #     if (period == 'date.day'){
#   #   a <- a %>% 
#   #     mutate(datetime = floor_date(datetime, unit = 'days')) %>%
#   #     group_by(datetime, .dots = groupers) %>% 
#   #     summarize_if(is.numeric, list(mean.val = mean.val,
#   #                                   low.val = low.val,
#   #                                   high.val = high.val))%>%
#   #     ungroup() %>%
#   #     mutate()
#   # }
# 
#   return(a)
# 
# }


    #   plot.monthly <- function(metric, data, location = NULL) {
    #  
    #           # define upper y-limit for plot based on metric
    #   y_range <- case_when(
    #     metric == 'pm25' ~ c(0,40),
    #     metric == 'voc' ~ voc_lim,
    #     metric == 'co2' ~ c(0,2000),
    #     metric == 'temp' ~ temp_lim,
    #     metric == 'humid' ~ humid_lim,
    #     metric == 'lux' ~ lux_lim,
    #     metric == 'spl_a' ~ spl_a_lim)
    #   
    #     #     y_label <- case_when(
    #     # metric == 'pm25' ~ expression('PM'[2.5]*', ppb'),
    #     # metric == 'voc' ~ 'TVOC, ppb',
    #     # metric == 'co2' ~ expression('CO'[2]*', ppb'),
    #     # metric == 'temp' ~ 'Temperature, deg C',
    #     # metric == 'humid' ~ 'Relative Humidity, %',
    #     # metric == 'lux' ~ 'Light, lx',
    #     # metric == 'spl_a' ~ 'Noise, dB')
    #   
    #  ggplot(data, aes(x = month, y = get(paste0(metric, '_mean.val')), color = home))+
    # geom_line( aes(group = home), size = 1)+
    # {if( is.null(location) | length(location) > 1) 
    #   facet_wrap(~factor(location, levels = c('living', 'kitchen', 'bedroom',
    #                                           'garage', 'outdoor')),
    #              ncol = 5)}+
    # ##geom_errorbar(aes(ymax = pm25_high.val, ymin = pm25_low.val))+ ##bars instead?
    # # geom_ribbon(aes(ymax = get(paste0(metric, '_high.val')),
    # #                 ymin = get(paste0(metric, '_low.val')), fill = home),
    # #             alpha = 0.2, color = NA)+
    # labs(y = paste('Average', metric),
    #      x = "Month",
    #      title = 'Monthly')+
    # scale_x_discrete(
    #                    labels = sapply(month.abb[c(1:12)],
    #                                    substr, start = 1, stop = 1) %>% unname(),
    #                    breaks = month.abb[c(1:12)]
    #                    )+
    #    scale_color_discrete(name = 'Home')+
    # theme_bw()+
    # theme(plot.title = element_blank(),
    #       title = element_text(size = medium),
    #       axis.text.y = element_text(size = small),
    #       axis.text.x = element_text(size = small-3),
    #       strip.text = element_text( size = medium),
    #       axis.title = element_text(size = medium),
    #       legend.title = element_text(size = medium-3),
    #       panel.spacing.x = unit(1, 'lines') # add horiz space between facets
    #       )+
    #            coord_cartesian(ylim = y_range)+
    #     # make point size proportional to # of obs, with 0 obs = size 0
    #     # geom_point(aes(size = n))+
    #     scale_size_area(max_size = max_point_size, guide = 'none')+
    #       ##for extra space between facets
    # theme(
    #       strip.background =element_blank())
    #   }
```

