---
title: "omni_hourly_correlation"
author: "Andrew Purgiel"
date: "7/22/2021"
output: html_document
---
---
title: "omni_hourly_correlation"
author: "Andrew Purgiel"
date: "1/13/2021"
output: html_document
---

```{r global_options, include=FALSE}
knitr::opts_chunk$set(fig.path = 'figures/',
  warning = FALSE,
  message = FALSE,
  echo = FALSE,
  fig.width = 10, fig.height = 3,
  cache = FALSE)
```

---

```{r libraries}
library(dplyr)
library(purrr)
library(tidyr)
library(openair)
library(ggplot2)
library(readr)
library(googlesheets4)
library(lubridate)
```

```{r data_import}
omni_hourly_data <- read_rds('./csv_created/omni_hourly_calibrated.rds')
```


```{r define_functions}

##Define a char vector of home numbers using a number vector,
##ex: x <- home.list(c(1:15)) for homes 1-15
threedig <- function(x) {
  if (nchar(x) == 1) {a <- paste0('00', x)
  return(a)
  }
  
  if (nchar(x) == 2) {a<- paste0('0', x)
  return(a)
  }
  else return(a)
}

home.list <- function(x) sapply(x, threedig)


 # function to extract a legend from one plot for use in whole plot grid
 # reference: https://stackoverflow.com/questions/13649473/add-a-common-legend-for-combined-ggplots
 g_legend<-function(a.gplot){
    tmp <- ggplot_gtable(ggplot_build(a.gplot))
    leg <- which(sapply(tmp$grobs, function(x) x$name) == "guide-box")
    legend <- tmp$grobs[[leg]]
    return(legend)}


 
 # between-room correlation functions--------------------------------------

 
# hourly correlation between two rooms
 room.hourly.plot <- function(data, hm, rmlist,
                              metric, method) { 
   
   ##function to find the correlation between room pair (y)
   ##in a home at a given hour (x)
   r.coeff.hour <- function(x,y) {
     a <-
       
       ##data from room 1
       data %>%
       filter(home == hm & room == y[1]) %>%
       
       ##join with data from room 2 based on timestamp
       full_join(
         data %>%
           filter(home == hm & room == y[2]),
         by = 'date',
         suffix = c('.1','.2'))
     
     ##make an hour column and filter data by hour of day
     a$hour <- a$date %>%
       hour()
     
     a <- a %>%
       filter(hour == x)
     
     ##calculate R coefficient of choice for room at the filtered hour
     b <- tryCatch(cor.test(a %>% pull(paste0(metric, '.1')),
                            a %>% pull(paste0(metric, '.2')),
                            method = method)$estimate,
                   error = function(e) NA)
     
     ##find p-value
     
     c <- tryCatch(cor.test(a %>% pull(paste0(metric, '.1')),
                            a %>% pull(paste0(metric, '.2')),
                            method = method)$p.value,
                   error = function(e) NA)
     
     
     return(cbind(b,c))
     
   }
   
   
   
   ##find correlation between room pair (z) by hour
   cor.tab.hour <- function (z) {
     
     a <- sapply(c(0:23), r.coeff.hour,
                            y = z)
     
     tibble('hour' = c(0:23),
            
            ##make a column for correlation coefficient values
            'col1' = a[1,],
            
            ##make a column for correlation p-values
            'col2' = a[2,]) %>%
       
       ##rename columns with names of compared rooms
       mutate(!!paste0(z[1],'-', z[2]) := col1,
              !!paste0(z[1],'-', z[2], '_p') := col2) %>%
       select(-col1, -col2)
   }
   
   ##find correlations and pvalues for each room pair
   a <- lapply(rmlist, cor.tab.hour) %>%
     
     ##megre all results into one table
     reduce(full_join, by = 'hour')
   
   ##make a melted table to prepare for plot
   a <-
     ##melt all the r-value columns
     a %>%
     as.data.frame() %>%
     select(hour, !ends_with('_p')) %>%
     melt(id.vars = 'hour') %>%
     mutate(r = value) %>%
     select(-value) %>%
     
     ##join with melted columns of p values
     full_join(
       a %>%
         as.data.frame() %>%
         select(hour, ends_with('_p')) %>%
         ##remove the '_p' from the id of the p-values
         rename_at(.vars = vars(ends_with('_p')),
                   .funs = ~sub('_p', "", .))%>%
         melt(id.vars = 'hour') %>%
         mutate(p = value) %>%
         select(-value),
       by = c('hour','variable')
     )
   
   ##from
   ##https://www.rdocumentation.org/packages/ggplot2/versions/1.0.1/topics/scale_colour_gradient2
   
   ggplot(a, aes(hour, r)) + 
     ggtitle(paste('Home', hm, metric))+
     geom_point(aes(size = ifelse(p < 0.05, 3, 1),
                    color = variable))+ 
     scale_size_identity() +
     coord_cartesian(ylim = c(0,1))+
     ylab(paste(method, 'correlation coefficient'))+
     theme_bw()+
     theme(axis.text.x = element_text(size = medium),
           axis.title.x = element_text(size = medium),
           axis.title.y = element_text(size = medium),
           axis.text.y = element_text(size = medium),
           plot.title = element_text(size = large, hjust = 0.5),
           legend.title = element_text(size = xsmall),
           legend.text = element_text(size = xsmall))+
     scale_color_discrete(name = 'Location Correlation')
 }
 
 
 
 
 ##function to plot in a grid
 plot.grid.rooms <- function (data, hms, rmlist, metric, method,
                        ncolumn) {
    plots <- lapply(hms, room.hourly.plot,
                    data = data, metric = metric,
                    rmlist = rmlist,
                    method = 'spearman'
                    )
    
    ##omit NULL values (from homes or rooms without valid data)
    plots <- plots[!sapply(plots, is.null)]
    
    legend <- g_legend(plots[[1]]) # extract legend from first plot
    
    # omit labels and such from plots
    plots <- lapply(plots,
                    function(myplot) {
                       
#                        # change existing title
# # https://stackoverflow.com/questions/41940000/modifying-ggplot-objects-after-creation
# myplot<- ggplot_build(myplot)
# 
# myplot$plot$labels$title <-
#    sub('.*Home ', '',myplot$plot$labels$title) %>% # extract characters after 'Home'
#    substr(1,3) # extract first three remaining characters (home number)
# 
# # convert back to a ggplot object
# myplot <- ggplot_gtable(myplot)
# myplot <- as_ggplot(myplot)

# change all other labels
                       myplot+
      theme(
         axis.text.x = element_text(size = xsmall),
            axis.text.y = element_text(size = xsmall),
           axis.title.x = element_blank(),
           axis.title.y = element_blank(),
           plot.title = element_text(size = xsmall, hjust = 0.5),
           legend.title = element_text(size = xsmall),
           legend.text = element_text(size = xsmall),
           legend.position = 'none')
                       
                       
                    }
    )
      
    # arrange all plots
    # reference: https://stackoverflow.com/questions/10706753/how-do-i-arrange-a-variable-list-of-plots-using-grid-arrange
    grid.arrange(arrangeGrob(grobs = plots),
                 legend, # add in legend
                 nrow=2, # one row for all plots, one row for legend
                 heights=c(10, 1), # second height is for legend
                 top = metric
    )
 }
 
 
 
 
# between-metric correlation functions--------------------------------------
 
 # data <- rtdata
 # hm <- '008'
 # rm <- 'living'
 # metric_pair_list <- list(c('co2', 'voc'), c('co2','light'))
 # hr <- 5
 # method <- 'pearson'
 
  data <- 'asdfas'
 hm <- 'asdfas'
 rm <- 'agasdfsdaf'
 metric_pair_list <- 'asdfasdfavgae'
 hr <- 'dfghdfg'
 method <- 'asvfadsfbawerb'
 


    # hourly correlation between two metrics
 metric.hourly.plot <- function(data, hm, rm,
                              metric_pair_list, method
                              ) { 
   
   ##function to find the correlation between metric pair
   ##in a home at a given hour 
   r.coeff.hour <- function(metric_pair1, hr) {
     a <-
       
       ##data from specified room in one home
       data %>%
       filter( room == rm & home == hm) %>%
     ##make an hour column and filter data by hour of day
     mutate(hour = hour(date)) %>%
       filter(hour == hr)
     
     # run correlation test with method of choice,
     # return NAs if not enough data fro an hour
     a <- tryCatch(cor.test(a %>% pull(all_of(metric_pair1[1])),
                            a %>% pull(all_of(metric_pair1[2])),
                            method = method),
                   error = function(e) list(estimate = NA, p.value = NA))
     
     ##calculate R coefficient of choice for room at the filtered hour
     b <- a$estimate
     
     ##find p-value
     
     c <- a$p.value
     
     
     return(cbind(b,c))
     
   }
   

   
   ##find correlation between metric pair (z) by hour
   cor.tab.hour <- function (metric_pair2) {
     
     a <- sapply(c(0:23), r.coeff.hour,
                            metric_pair1 = metric_pair2)
     
     tibble('hour' = c(0:23),
            
            ##make a column for correlation coefficient values
            'col1' = a[1,],
            
            ##make a column for correlation p-values
            'col2' = a[2,]) %>%
       
       ##rename columns with names of compared rooms
       mutate(!!paste0(metric_pair2[1],'-', metric_pair2[2]) := col1,
              !!paste0(metric_pair2[1],'-', metric_pair2[2], '_p') := col2) %>%
       select(-col1, -col2)
   }
   
   ##find correlations and pvalues for each metric pair
   a <- lapply(metric_pair_list, cor.tab.hour) %>%
     
     ##megre all results into one table
     reduce(full_join, by = 'hour')
   
   ##make a melted table to prepare for plot
   a <-
     ##melt all the r-value columns
     a %>%
     as.data.frame() %>%
     select(hour, !ends_with('_p')) %>%
     melt(id.vars = 'hour') %>%
     mutate(r = value) %>%
     select(-value) %>%
     
     ##join with melted columns of p values
     full_join(
       a %>%
         as.data.frame() %>%
         select(hour, ends_with('_p')) %>%
         ##remove the '_p' from the id of the p-values
         rename_at(.vars = vars(ends_with('_p')),
                   .funs = ~sub('_p', "", .))%>%
         melt(id.vars = 'hour') %>%
         mutate(p = value) %>%
         select(-value),
       by = c('hour','variable')
     )
   
   ##from
   ##https://www.rdocumentation.org/packages/ggplot2/versions/1.0.1/topics/scale_colour_gradient2
      ggplot(a, aes(hour, r)) + 
     ggtitle(paste('Home', hm, rm))+
     geom_point(aes(size = ifelse(p < 0.05, 3, 1),
                    color = variable))+ 
     scale_size_identity() +
     coord_cartesian(ylim = c(0,1))+
     ylab(paste(method, 'correlation coefficient'))+
     theme_bw()+
     theme(axis.text.x = element_text(size = medium),
           axis.title.x = element_text(size = medium),
           axis.title.y = element_text(size = medium),
           axis.text.y = element_text(size = medium),
           plot.title = element_text(size = large, hjust = 0.5),
           legend.title = element_text(size = xsmall),
           legend.text = element_text(size = xsmall))+
     scale_color_discrete(name = 'Metric Correlation')
   
   
 }
 
 ##function to plot in a grid
 plot.grid.metrics <- function (data, hms, rm, metric_pair_list, method,
                        ncolumn) {
    plots <- lapply(hms, metric.hourly.plot,
                    data = data, rm = rm,
                    metric_pair_list = metric_pair_list,
                    method = 'spearman'
                    )
    
    ##omit NULL values (from homes or rooms without valid data)
    plots <- plots[!sapply(plots, is.null)]
    
    legend <- g_legend(plots[[1]]) # extract legend from first plot
    
    # omit labels and such from plots
    plots <- lapply(plots,
                    function(myplot) {
                       
#                        # change existing title
# # https://stackoverflow.com/questions/41940000/modifying-ggplot-objects-after-creation
# myplot<- ggplot_build(myplot)
# 
# myplot$plot$labels$title <-
#    sub('.*Home ', '',myplot$plot$labels$title) %>% # extract characters after 'Home'
#    substr(1,3) # extract first three remaining characters (home number)
# 
# # convert back to a ggplot object
# myplot <- ggplot_gtable(myplot)
# myplot <- as_ggplot(myplot)

# change all other labels
                       myplot+
      theme(
         axis.text.x = element_text(size = xsmall),
            axis.text.y = element_text(size = xsmall),
           axis.title.x = element_blank(),
           axis.title.y = element_blank(),
           plot.title = element_text(size = xsmall, hjust = 0.5),
           legend.title = element_text(size = xsmall),
           legend.text = element_text(size = xsmall),
           legend.position = 'none')
                       
                       
                    }
    )
      
    # arrange all plots
    # reference: https://stackoverflow.com/questions/10706753/how-do-i-arrange-a-variable-list-of-plots-using-grid-arrange
    grid.arrange(arrangeGrob(grobs = plots),
                 legend, # add in legend
                 nrow=2, # one row for all plots, one row for legend
                 heights=c(10, 1), # second height is for legend
                 top = rm
    )
 }
 

###############
 
 
 

#  # testing methods
#  start <- Sys.time()
# metric.hourly.plot(hourly, '008', 'living',
#                              list(c('co2', 'voc'), c('co2','light')), 'spearman',
#                    simple = TRUE)
#  end <- Sys.time()
# 
#  run_time2 <- end - start
# 
#  all.equal(test1, test2)

```

```{r define_variables, include = FALSE}

#define list of homes for analysis
all_homes <- home.list(1:16)

some_homes <- home.list(c(1,3,6,8,12,15))

##define room pairs for comparison
rms_1 <- c('kitchen', 'living')
rms_2 <- c('kitchen', 'garage')
rms_3 <- c('kitchen', 'bedroom')
rms_4 <- c('outdoor', 'living')
rms_5 <- c('outdoor', 'garage')
rms_6 <- c('outdoor', 'bedroom')
rms_7 <- c('garage', 'living')
rms_8 <- c('garage', 'bedroom')
rms_9 <- c('living', 'bedroom')

######make lists of rooms by defining which pairs to compare
#comparison of 'living areas'
rms_indoor <- lapply(c(1,3,9), function(x) get(paste0('rms_', x)))
#comparison
rms_driver <- lapply(c(1,4,7), function(x) get(paste0('rms_', x)))

##For labeling pruposes
xsmall <- 6
small <- 15
medium <- 20
large <- 26

# # for looking at seasons
# fall <- c('2020-09-21 00:00:00', '2020-12-20 23:59:59')
# winter <- c('2020-12-21 00:00:00', '2020-3-20 23:59:59')
# 
# 
# hourly_fall <- hourly%>%
#    filter(between(as.POSIXct(date),
#                   as.POSIXct(fall[1], format = "%Y-%m-%d %H:%M:%S", tz = "US/Mountain"),
#                   as.POSIXct(fall[2], format = "%Y-%m-%d %H:%M:%S", tz = "US/Mountain")))
# 
# 
# hourly_winter <- hourly %>%
#    filter(between(as.POSIXct(date),
#                   as.POSIXct(winter[1], format = "%Y-%m-%d %H:%M:%S", tz = "US/Mountain"),
#                   as.POSIXct(winter[2], format = "%Y-%m-%d %H:%M:%S", tz = "US/Mountain")))


```

```{r functions_correlation_additional variable, eval = TRUE}
data <- omni_hourly_data
hm <- '008'
rm_pair <- c('living', 'garage')
met <- 'pm25'
method <- 'spearman'
hr <- 23

##in a home at a given hour 
 r.coeff.hour <- function(data, hm, rm_pair,
                          hr, met,
                          method = 'spearman') {
   hour_data <-
     data %>%
     filter(home == hm) %>%
     select(datehour, home, location, all_of(met)) %>%
     pivot_wider(names_from = location, values_from = all_of(met)) %>%
   
      ##make an hour column and filter data by hour of day
     mutate(hour = hour(datehour)) %>%
     filter(hour == hr)
   
      ##calculate R coefficient of choice for room at the filtered hour
   cor_results <- tryCatch(
     {
     a <- cor.test(hour_data %>% pull(rm_pair[1]),
                          hour_data %>% pull(rm_pair[2]),
                          method = method)
     # return results
     tibble('coeff' = a[['estimate']],
            'p_val' = a[['p.value']],
            'method' = method)
     },
                 error = function(e) {
                   # return empty values if error
                   tibble('coeff' = NA,
            'p_val' = NA,
            'method' = method)
                 })
    return(cor_results)

    }
 

 
 ##find correlation between room pair  by hour
 cor.tab.hour <- function (data, hm, rm_pair,
                           metric, method) {
   tibble('hour' = c(0:23),
          
          ##make a column for correlation coefficient values
          'col1' = sapply(c(0:23), r.coeff.hour,
                          data = data,
                          hm = hm,
                          metric = metric,
                          method = method,
                          rm_pair = rm_pair)[1,],
          
          ##make a column for correlation p-values
          'col2' = sapply(c(0:23),r.coeff.hour,
                          data = data,
                          hm = hm,
                          metric = metric,
                          method = method,
                          rm_pair = rm_pair)[2,]) %>%
     
     ##rename columns with names of compared rooms
     mutate(!!paste0(rm_pair[1],'-', rm_pair[2]) := col1,
            !!paste0(rm_pair[1],'-', rm_pair[2], '_p') := col2) %>%
     select(-col1, -col2)
 }

 
 
 
 
 ##function to create a plot of correlation between
 ##multiple room pairs by hour
 ##with additional variable also plotted by hour
 

 
 
##Temp
 room.hourly.plot.temp <- function (data, hm, rmlist, metric, method) {
   
   ##find correlations and pvalues for each room pair
   a <- lapply(rmlist, cor.tab.hour,
               data = data,
               hm = hm,
               metric = metric,
               method = method) %>%
     
     ##megre all results into one table
     reduce(full_join, by = 'hour')
   
   ##make a melted table to prepare for plot
   a <-
     ##melt all the r-value columns
     a %>%
     as.data.frame() %>%
     select(hour, !ends_with('_p')) %>%
     melt(id.vars = 'hour') %>%
     mutate(r = value) %>%
     select(-value) %>%
     
     ##join with melted columns of p values
     full_join(
       a %>%
         as.data.frame() %>%
         select(hour, ends_with('_p')) %>%
         ##remove the '_p' from the id of the p-values
         rename_at(.vars = vars(ends_with('_p')),
                   .funs = ~sub('_p', "", .))%>%
         melt(id.vars = 'hour') %>%
         mutate(p = value) %>%
         select(-value),
       by = c('hour','variable')
     ) %>%
     
     ##join with average hourly kitchen co2
     full_join(
       hourly %>%
         filter(home == hm, room == 'outdoor') %>%
         select(date, co2, temp, rh) %>%
         mutate(hour = hour(date)) %>%
         group_by(hour) %>%
         summarize(co2 = mean(co2, na.rm = TRUE),
                   temp = mean(temp, na.rm = TRUE),
                   rh = mean(rh, na.rm = TRUE)) %>%
         ungroup()
     )
   
   
   ##add coefficient to scale kitchen CO2 axis for two y axes
   coeff <- 50
   
   
   ggplot(a, aes(x = hour)) + 
     ggtitle(hm)+
     geom_point(aes(y = r, size = ifelse(p < 0.05, 3, 1),
                    color = variable))+ 
     ##add points for CO2 levels in kitchen
     geom_point(aes(y = temp/coeff, shape = 'outdoor T'))+
     scale_size_identity() +
     coord_cartesian(ylim = c(0,1))+
     ylab(expression("Spearman's"~rho))+
     theme_bw()+
     scale_color_discrete(name = 'Location Correlation')+
     scale_y_continuous(
       
       # Add a second axis and specify its features
       sec.axis = sec_axis( trans=~.*coeff,
                            name = 'deg C')
       )+
     #remove label for second legend
     scale_shape_manual(NULL, values = 16)
 }
 
 

 
 
  ##functions that omit legends and lables to plot in a grid


 #Temp
 room.hourly.plot.temp.simp <- function (data, hm, rmlist, metric, method) {
   
   ##find correlations and pvalues for each room pair
   a <- lapply(rmlist, cor.tab.hour,
               data = data,
               hm = hm,
               metric = metric,
               method = method) %>%
     
     ##megre all results into one table
     reduce(full_join, by = 'hour')
   
   ##make a melted table to prepare for plot
   a <-
     ##melt all the r-value columns
     a %>%
     as.data.frame() %>%
     select(hour, !ends_with('_p')) %>%
     melt(id.vars = 'hour') %>%
     mutate(r = value) %>%
     select(-value) %>%
     
     ##join with melted columns of p values
     full_join(
       a %>%
         as.data.frame() %>%
         select(hour, ends_with('_p')) %>%
         ##remove the '_p' from the id of the p-values
         rename_at(.vars = vars(ends_with('_p')),
                   .funs = ~sub('_p', "", .))%>%
         melt(id.vars = 'hour') %>%
         mutate(p = value) %>%
         select(-value),
       by = c('hour','variable')
     ) %>%
     
     ##join with average hourly kitchen co2
     full_join(
       hourly %>%
         filter(home == hm, room == 'outdoor') %>%
         select(date, co2, temp, rh) %>%
         mutate(hour = hour(date)) %>%
         group_by(hour) %>%
         summarize(co2 = mean(co2, na.rm = TRUE),
                   temp = mean(temp, na.rm = TRUE),
                   rh = mean(rh, na.rm = TRUE)) %>%
         ungroup()
     )
   
   
   ##add coefficient to scale kitchen CO2 axis for two y axes
   coeff <- 50
   
   
   ggplot(a, aes(x = hour)) + 
     ggtitle(hm)+
     geom_point(aes(y = r, size = ifelse(p < 0.05, 3, 1),
                    color = variable))+ 
     ##add points for CO2 levels in kitchen
     geom_point(aes(y = temp/coeff, shape = 'outdoor T'))+
     scale_size_identity() +
     coord_cartesian(ylim = c(0,1))+
     ylab(expression("Spearman's"~rho))+
     theme_bw()+
     theme(axis.title = element_blank(),
           axis.text = element_blank(),
           legend.position = 'none')+
     scale_color_discrete(name = 'Location Correlation')+
     scale_y_continuous(
       
       # Add a second axis and specify its features
       sec.axis = sec_axis( trans=~.*coeff,
                            name = 'deg C')
     )+
     #remove label for second legend
     scale_shape_manual(NULL, values = 16)
 }
 
  ##function to plot in a grid
 room.hourly.plot.grid <- function (data, hms, rmlist, metric, method,
                                       func, ncolumn) {
   plots <- lapply(hms, func,
                   data = data, rmlist = rmlist,
                   metric = metric, method = method)
   
   ##omit NULL values (from homes or rooms without valid data)
   plots <- plots[!sapply(plots, is.null)]
   
   
   do.call('grid.arrange', c(plots, ncol = ncolumn))
 }

```


# Hourly Between-Room Correlation Plots  

* plots are based on **hourly** average values
* separate plot for each house
* only a selection of houses



## Indoor Areas  




### room-room hourly correlation multiple homes


```{r between_room_hour_correlations_living_plot, warning=FALSE, eval = TRUE}
##make plot for some homes
 ###"living areas'
 #pm25
 lapply(some_homes, room.hourly.plot,
        data = hourly, rmlist = rms_indoor,
        metric = 'pm25', 'spearman')

 
 #voc
 lapply(some_homes, room.hourly.plot,
        data = hourly, rmlist = rms_indoor,
        metric = 'voc', 'spearman')
 

```

### Possible Takeaways  

* no obvious trends in PM2.5 indoor-indoor strength of directional correlations
* VOC directional indoor-indoor correlation gets weaker in some homes late evening (8pm)

### Between Room by Hour- "Interaction Areas"  

```{r between_room_hour_correlations_drivers_plot, warning=FALSE, eval = TRUE}
 ###'drivers'
 #'pm25
 lapply(some_homes, room.hourly.plot,
        data = hourly, rmlist = rms_driver,
        metric = 'pm25', 'spearman')
  
 #voc
 lapply(some_homes, room.hourly.plot,
        data = hourly, rmlist = rms_driver,
        metric = 'voc', 'searman')
```

### All homes

```{r between_room_hour_correlations_grid, warning=FALSE, eval = TRUE}
 
 # test for one metric
grid <- plot.grid.rooms(hourly, all_homes, rms_driver, 'pm25',
          'spearman', ncolumn = 4)
 ggsave(paste0('hourly_corr_test', Sys.Date(),'.pdf'), grid,
          height = 8, width = 10)

    
    all_metrics <- c('pm25', 'voc', 'co2', 'temp','rh', 'light', 'noise')
    
    rm_pairs <- rms_driver
    
    # make plot grid and save for all metrics
lapply(all_metrics, function(metric){
   
        grid <- plot.grid.rooms(hourly, all_homes, rm_pairs, metric,
          'spearman', ncolumn = 4)
 
 
    ggsave(paste0('hourly_corr_',metric,'_', Sys.Date(),'.pdf'), grid,
          height = 8, width = 10)
}
)
       
 





```



### Possible Takeaways  
* **in many homes, PM2.5 directional correlation for garage and outdoor to livingroom peaks near 6am, trends downward until mid-night, then starts to increase again**  


### Between Room By Hour- With Additional Variable  

```{r functions_correlation_additional variable, eval = TRUE}

##in a home at a given hour 
 r.coeff.hour <- function(data, hm, rm_pair,
                          hr, metric, method) {
   a <-
     
     ##data from room 1
     data %>%
     filter(home == hm & room == rm_pair[1]) %>%
     
     ##join with data from room 2 based on timestamp
     full_join(
       data %>%
         filter(home == hm & room == rm_pair[2]),
       by = 'date',
       suffix = c('.1','.2'))
   
   ##make an hour column and filter data by hour of day
   a$hour <- a$date %>%
     hour()
   
   a <- a %>%
     filter(hour == hr)
   
   ##calculate R coefficient of choice for room at the filtered hour
   b <- tryCatch(cor.test(a %>% pull(paste0(metric, '.1')),
                          a %>% pull(paste0(metric, '.2')),
                          method = method)$estimate,
                 error = function(e) NA)
   
   ##find p-value
   
   c <- tryCatch(cor.test(a %>% pull(paste0(metric, '.1')),
                          a %>% pull(paste0(metric, '.2')),
                          method = method)$p.value,
                 error = function(e) NA)
   
   
   return(cbind(b,c))
   
 }
 

 
 
 ##find correlation between room pair  by hour
 cor.tab.hour <- function (data, hm, rm_pair,
                           metric, method) {
   tibble('hour' = c(0:23),
          
          ##make a column for correlation coefficient values
          'col1' = sapply(c(0:23), r.coeff.hour,
                          data = data,
                          hm = hm,
                          metric = metric,
                          method = method,
                          rm_pair = rm_pair)[1,],
          
          ##make a column for correlation p-values
          'col2' = sapply(c(0:23),r.coeff.hour,
                          data = data,
                          hm = hm,
                          metric = metric,
                          method = method,
                          rm_pair = rm_pair)[2,]) %>%
     
     ##rename columns with names of compared rooms
     mutate(!!paste0(rm_pair[1],'-', rm_pair[2]) := col1,
            !!paste0(rm_pair[1],'-', rm_pair[2], '_p') := col2) %>%
     select(-col1, -col2)
 }

 
 
 
 
 ##function to create a plot of correlation between
 ##multiple room pairs by hour
 ##with additional variable also plotted by hour
 
 #co2
 room.hourly.plot.co <- function (data, hm, rmlist, metric, method) {
   
   ##find correlations and pvalues for each room pair
   a <- lapply(rmlist, cor.tab.hour,
               data = data,
               hm = hm,
               metric = metric,
               method = method) %>%
     
     ##megre all results into one table
     reduce(full_join, by = 'hour')
   
   ##make a melted table to prepare for plot
   a <-
     ##melt all the r-value columns
     a %>%
     as.data.frame() %>%
     select(hour, !ends_with('_p')) %>%
     melt(id.vars = 'hour') %>%
     mutate(r = value) %>%
     select(-value) %>%
     
     ##join with melted columns of p values
     full_join(
       a %>%
         as.data.frame() %>%
         select(hour, ends_with('_p')) %>%
         ##remove the '_p' from the id of the p-values
         rename_at(.vars = vars(ends_with('_p')),
                   .funs = ~sub('_p', "", .))%>%
         melt(id.vars = 'hour') %>%
         mutate(p = value) %>%
         select(-value),
       by = c('hour','variable')
     ) %>%
     
     ##join with average hourly kitchen co2
     full_join(
       hourly %>%
         filter(home == hm, room == 'kitchen') %>%
         select(date, co2, temp, rh) %>%
         mutate(hour = hour(date)) %>%
         group_by(hour) %>%
         summarize(co2 = mean(co2, na.rm = TRUE),
                   temp = mean(temp, na.rm = TRUE),
                   rh = mean(rh, na.rm = TRUE)) %>%
         ungroup()
     )
   
   
   ##add coefficient to scale kitchen CO2 axis for two y axes
   coeff <- 2000
   
   
   ggplot(a, aes(x = hour)) + 
     ggtitle(hm)+
     geom_point(aes(y = r, size = ifelse(p < 0.05, 3, 1),
                    color = variable))+ 
     ##add points for CO2 levels in kitchen
     geom_point(aes(y = co2/coeff, shape = 'kitchen CO2'))+
     scale_size_identity() +
     coord_cartesian(ylim = c(0,1))+
     ylab(expression("Spearman's"~rho))+
     theme_bw()+
     scale_color_discrete(name = 'Location Correlation')+
     scale_y_continuous(
       
       # Add a second axis and specify its features
       sec.axis = sec_axis( trans=~.*coeff,
                            name = 'ppb')
     )+
     #remove label for second legend
     scale_shape_manual(NULL, values = 16,
                        label = expression('kitchen CO'[2]))
 }
 
 
##Temp
 room.hourly.plot.temp <- function (data, hm, rmlist, metric, method) {
   
   ##find correlations and pvalues for each room pair
   a <- lapply(rmlist, cor.tab.hour,
               data = data,
               hm = hm,
               metric = metric,
               method = method) %>%
     
     ##megre all results into one table
     reduce(full_join, by = 'hour')
   
   ##make a melted table to prepare for plot
   a <-
     ##melt all the r-value columns
     a %>%
     as.data.frame() %>%
     select(hour, !ends_with('_p')) %>%
     melt(id.vars = 'hour') %>%
     mutate(r = value) %>%
     select(-value) %>%
     
     ##join with melted columns of p values
     full_join(
       a %>%
         as.data.frame() %>%
         select(hour, ends_with('_p')) %>%
         ##remove the '_p' from the id of the p-values
         rename_at(.vars = vars(ends_with('_p')),
                   .funs = ~sub('_p', "", .))%>%
         melt(id.vars = 'hour') %>%
         mutate(p = value) %>%
         select(-value),
       by = c('hour','variable')
     ) %>%
     
     ##join with average hourly kitchen co2
     full_join(
       hourly %>%
         filter(home == hm, room == 'outdoor') %>%
         select(date, co2, temp, rh) %>%
         mutate(hour = hour(date)) %>%
         group_by(hour) %>%
         summarize(co2 = mean(co2, na.rm = TRUE),
                   temp = mean(temp, na.rm = TRUE),
                   rh = mean(rh, na.rm = TRUE)) %>%
         ungroup()
     )
   
   
   ##add coefficient to scale kitchen CO2 axis for two y axes
   coeff <- 50
   
   
   ggplot(a, aes(x = hour)) + 
     ggtitle(hm)+
     geom_point(aes(y = r, size = ifelse(p < 0.05, 3, 1),
                    color = variable))+ 
     ##add points for CO2 levels in kitchen
     geom_point(aes(y = temp/coeff, shape = 'outdoor T'))+
     scale_size_identity() +
     coord_cartesian(ylim = c(0,1))+
     ylab(expression("Spearman's"~rho))+
     theme_bw()+
     scale_color_discrete(name = 'Location Correlation')+
     scale_y_continuous(
       
       # Add a second axis and specify its features
       sec.axis = sec_axis( trans=~.*coeff,
                            name = 'deg C')
       )+
     #remove label for second legend
     scale_shape_manual(NULL, values = 16)
 }
 
 
 ##RH
 room.hourly.plot.rh <- function (data, hm, rmlist, metric, method) {
   
   ##find correlations and pvalues for each room pair
   a <- lapply(rmlist, cor.tab.hour,
               data = data,
               hm = hm,
               metric = metric,
               method = method) %>%
     
     ##megre all results into one table
     reduce(full_join, by = 'hour')
   
   ##make a melted table to prepare for plot
   a <-
     ##melt all the r-value columns
     a %>%
     as.data.frame() %>%
     select(hour, !ends_with('_p')) %>%
     melt(id.vars = 'hour') %>%
     mutate(r = value) %>%
     select(-value) %>%
     
     ##join with melted columns of p values
     full_join(
       a %>%
         as.data.frame() %>%
         select(hour, ends_with('_p')) %>%
         ##remove the '_p' from the id of the p-values
         rename_at(.vars = vars(ends_with('_p')),
                   .funs = ~sub('_p', "", .))%>%
         melt(id.vars = 'hour') %>%
         mutate(p = value) %>%
         select(-value),
       by = c('hour','variable')
     ) %>%
     
     ##join with average hourly kitchen co2
     full_join(
       hourly %>%
         filter(home == hm, room == 'outdoor') %>%
         select(date, co2, temp, rh) %>%
         mutate(hour = hour(date)) %>%
         group_by(hour) %>%
         summarize(co2 = mean(co2, na.rm = TRUE),
                   temp = mean(temp, na.rm = TRUE),
                   rh = mean(rh, na.rm = TRUE)) %>%
         ungroup()
     )
   
   
   ##add coefficient to scale kitchen CO2 axis for two y axes
   coeff <- 100
   
   
   ggplot(a, aes(x = hour)) + 
     ggtitle(hm)+
     geom_point(aes(y = r, size = ifelse(p < 0.05, 3, 1),
                    color = variable))+ 
     ##add points for CO2 levels in kitchen
     geom_point(aes(y = rh/coeff, shape = 'outdoor RH'))+
     scale_size_identity() +
     coord_cartesian(ylim = c(0,1))+
     ylab(expression("Spearman's"~rho))+
     theme_bw()+
     scale_color_discrete(name = 'Location Correlation')+
     scale_y_continuous(
       
       # Add a second axis and specify its features
       sec.axis = sec_axis( trans=~.*coeff,
                            name = '%')
     )+
     #remove label for second legend
     scale_shape_manual(NULL, values = 16)
 }
 
 
 
  ##functions that omit legends and lables to plot in a grid

 #CO2
 room.hourly.plot.co.simp <- function (data, hm, rmlist, metric, method) {
   
 ##find correlations and pvalues for each room pair
 a <- lapply(rmlist, cor.tab.hour,
             data = data,
             hm = hm,
             metric = metric,
             method = method) %>%
   
   ##megre all results into one table
   reduce(full_join, by = 'hour')
 
 ##make a melted table to prepare for plot
 a <-
   ##melt all the r-value columns
   a %>%
   as.data.frame() %>%
   select(hour, !ends_with('_p')) %>%
   melt(id.vars = 'hour') %>%
   mutate(r = value) %>%
   select(-value) %>%
   
   ##join with melted columns of p values
   full_join(
     a %>%
       as.data.frame() %>%
       select(hour, ends_with('_p')) %>%
       ##remove the '_p' from the id of the p-values
       rename_at(.vars = vars(ends_with('_p')),
                 .funs = ~sub('_p', "", .))%>%
       melt(id.vars = 'hour') %>%
       mutate(p = value) %>%
       select(-value),
     by = c('hour','variable')
   ) %>%
   
   ##join with average hourly kitchen co2
   full_join(
     hourly %>%
       filter(home == hm, room == 'kitchen') %>%
       select(date, co2) %>%
       mutate(hour = hour(date)) %>%
       group_by(hour) %>%
       summarize(co2 = mean(co2, na.rm = TRUE)) %>%
       ungroup()
   )
 

 ##add coefficient to scale kitchen CO2 axis for two y axes
 coeff <- 2000
 
 
 ggplot(a, aes(x = hour)) + 
   ggtitle(hm)+
   geom_point(aes(y = r, size = ifelse(p < 0.05, 3, 1),
                  color = variable))+ 
   ##add points for CO2 levels in kitchen
   geom_point(aes(y = co2/coeff))+
   scale_size_identity() +
   coord_cartesian(ylim = c(0,1))+
   ylab(expression("Spearman's"~rho))+
   theme_bw()+
   theme(axis.title = element_blank(),
         axis.text = element_blank(),
         legend.position = 'none')+
   scale_color_discrete(name = 'Location Correlation')+
   scale_y_continuous(
     
     # Add a second axis and specify its features
     sec.axis = sec_axis( trans=~.*coeff)
   )
 }
 
 #Temp
 room.hourly.plot.temp.simp <- function (data, hm, rmlist, metric, method) {
   
   ##find correlations and pvalues for each room pair
   a <- lapply(rmlist, cor.tab.hour,
               data = data,
               hm = hm,
               metric = metric,
               method = method) %>%
     
     ##megre all results into one table
     reduce(full_join, by = 'hour')
   
   ##make a melted table to prepare for plot
   a <-
     ##melt all the r-value columns
     a %>%
     as.data.frame() %>%
     select(hour, !ends_with('_p')) %>%
     melt(id.vars = 'hour') %>%
     mutate(r = value) %>%
     select(-value) %>%
     
     ##join with melted columns of p values
     full_join(
       a %>%
         as.data.frame() %>%
         select(hour, ends_with('_p')) %>%
         ##remove the '_p' from the id of the p-values
         rename_at(.vars = vars(ends_with('_p')),
                   .funs = ~sub('_p', "", .))%>%
         melt(id.vars = 'hour') %>%
         mutate(p = value) %>%
         select(-value),
       by = c('hour','variable')
     ) %>%
     
     ##join with average hourly kitchen co2
     full_join(
       hourly %>%
         filter(home == hm, room == 'outdoor') %>%
         select(date, co2, temp, rh) %>%
         mutate(hour = hour(date)) %>%
         group_by(hour) %>%
         summarize(co2 = mean(co2, na.rm = TRUE),
                   temp = mean(temp, na.rm = TRUE),
                   rh = mean(rh, na.rm = TRUE)) %>%
         ungroup()
     )
   
   
   ##add coefficient to scale kitchen CO2 axis for two y axes
   coeff <- 50
   
   
   ggplot(a, aes(x = hour)) + 
     ggtitle(hm)+
     geom_point(aes(y = r, size = ifelse(p < 0.05, 3, 1),
                    color = variable))+ 
     ##add points for CO2 levels in kitchen
     geom_point(aes(y = temp/coeff, shape = 'outdoor T'))+
     scale_size_identity() +
     coord_cartesian(ylim = c(0,1))+
     ylab(expression("Spearman's"~rho))+
     theme_bw()+
     theme(axis.title = element_blank(),
           axis.text = element_blank(),
           legend.position = 'none')+
     scale_color_discrete(name = 'Location Correlation')+
     scale_y_continuous(
       
       # Add a second axis and specify its features
       sec.axis = sec_axis( trans=~.*coeff,
                            name = 'deg C')
     )+
     #remove label for second legend
     scale_shape_manual(NULL, values = 16)
 }
 
 
 ##RH
 room.hourly.plot.rh.simp <- function (data, hm, rmlist, metric, method) {
   
   ##find correlations and pvalues for each room pair
   a <- lapply(rmlist, cor.tab.hour,
               data = data,
               hm = hm,
               metric = metric,
               method = method) %>%
     
     ##megre all results into one table
     reduce(full_join, by = 'hour')
   
   ##make a melted table to prepare for plot
   a <-
     ##melt all the r-value columns
     a %>%
     as.data.frame() %>%
     select(hour, !ends_with('_p')) %>%
     melt(id.vars = 'hour') %>%
     mutate(r = value) %>%
     select(-value) %>%
     
     ##join with melted columns of p values
     full_join(
       a %>%
         as.data.frame() %>%
         select(hour, ends_with('_p')) %>%
         ##remove the '_p' from the id of the p-values
         rename_at(.vars = vars(ends_with('_p')),
                   .funs = ~sub('_p', "", .))%>%
         melt(id.vars = 'hour') %>%
         mutate(p = value) %>%
         select(-value),
       by = c('hour','variable')
     ) %>%
     
     ##join with average hourly kitchen co2
     full_join(
       hourly %>%
         filter(home == hm, room == 'outdoor') %>%
         select(date, co2, temp, rh) %>%
         mutate(hour = hour(date)) %>%
         group_by(hour) %>%
         summarize(co2 = mean(co2, na.rm = TRUE),
                   temp = mean(temp, na.rm = TRUE),
                   rh = mean(rh, na.rm = TRUE)) %>%
         ungroup()
     )
   
   
   ##add coefficient to scale kitchen CO2 axis for two y axes
   coeff <- 100
   
   
   ggplot(a, aes(x = hour)) + 
     ggtitle(hm)+
     geom_point(aes(y = r, size = ifelse(p < 0.05, 3, 1),
                    color = variable))+ 
     ##add points for CO2 levels in kitchen
     geom_point(aes(y = rh/coeff, shape = 'outdoor RH'))+
     scale_size_identity() +
     coord_cartesian(ylim = c(0,1))+
     ylab(expression("Spearman's"~rho))+
     theme_bw()+
     theme(axis.title = element_blank(),
           axis.text = element_blank(),
           legend.position = 'none')+
     scale_color_discrete(name = 'Location Correlation')+
     scale_y_continuous(
       
       # Add a second axis and specify its features
       sec.axis = sec_axis( trans=~.*coeff,
                            name = '%')
     )+
     #remove label for second legend
     scale_shape_manual(NULL, values = 16)
 }
 
 
 
 
 
 ##function to plot in a grid
 room.hourly.plot.grid <- function (data, hms, rmlist, metric, method,
                                       func, ncolumn) {
   plots <- lapply(hms, func,
                   data = data, rmlist = rmlist,
                   metric = metric, method = method)
   
   ##omit NULL values (from homes or rooms without valid data)
   plots <- plots[!sapply(plots, is.null)]
   
   
   do.call('grid.arrange', c(plots, ncol = ncolumn))
 }

```

#### Different continuous variables,
#### one home examples


```{r correlation_additional_variable, eval = TRUE}

###all for one home

 room.hourly.plot.co(hourly, '003', list(c('outdoor','living')),
                     'pm25_ihs', 'pearson')

 room.hourly.plot.temp(hourly, '003', list(c('outdoor','living')),
                                            'pm25_ihs', 'pearson')
 
  room.hourly.plot.rh(hourly, '003', list(c('outdoor','living')),
                                            'pm25_ihs', 'pearson')
```

#### All homes (with Outdoor Temperature plotted as well)

```{r correlation_temp_grid, eval = TRUE}
 room.hourly.plot.grid(hourly, all_homes, list(c('outdoor', 'living')),
                                            'pm25_ihs', 'pearson',
                       room.hourly.plot.temp.simp, 3)

```



# Between-metric hourly correlation

```{r between_metric_hour_correlations, warning=FALSE, eval = TRUE}


# # test function for one room
# grid <- plot.grid.metrics(hourly, all_homes, 'garage',
#           list(c('co2', 'voc'), c('co2','light')),
#           'spearman', ncolumn = 4)
#  ggsave(paste0('hourly_corr_test', Sys.Date(),'.pdf'), grid,
#           height = 8, width = 10)

    
    all_rooms <- c('bedroom', 'living', 'kitchen', 'garage', 'outdoor')
    
    metric_pairs <- list(c('co2', 'voc'), c('co2','light'), c('co2','noise'))
    
    # make plot grid and save for all rooms
lapply(all_rooms, function(room){
   
        grid <- plot.grid.metrics(hourly, all_homes, room,
          metric_pairs,
          'spearman', ncolumn = 4)
 
 
    ggsave(paste0('hourly_corr_',room,'_', Sys.Date(),'.pdf'), grid,
          height = 8, width = 10)
}
)
       
 


```

