---
title: "Soot Scan - Testing"
output:
  html_document:
    toc: true
    toc_float: true
    theme: paper
---

```{r global_options, include=FALSE}
knitr::opts_chunk$set(fig.path = 'figures/',
  warning = FALSE,
  message = FALSE,
  echo = FALSE,
  fig.width = 10, fig.height = 4,
  cache = FALSE)
```

```{r}
library(dplyr)
library(purrr)
library(tidyr)
library(openair)
library(ggplot2)
library(readr)
library(lubridate)
```

---

# Read data

```{r}
files <- list.files("../../data/filters", ".*soot_scan.*.csv$", full.names = "TRUE")
```

```{r}
nice_names <- function(x){gsub(" ", "_", tolower(x))}
```

```{r}
df <- read_csv(files[2], col_types = cols()) %>%
  rename_all(nice_names) %>%
  mutate(rep = as.factor(rep),
         date = as.factor(date))
```

* `r length(unique(df$filter_id))` unloaded filters,  repeated soot scan measurements

# Plot

```{r fig_total_kwh}
ggplot(df, aes(x = filter_id, y = ir, color = date)) +
  geom_point() +
  theme_bw()
```


# Variability 

* remove first 3 measurements (instrument warming up)

```{r}
df_clean <- df %>% 
  filter (!(filter_id == "001" & rep == "1")) %>%
  filter (!(filter_id == "002" & rep == "1")) %>%
  filter (!(filter_id == "003" & rep == "1")) %>%
  group_by(filter_id, date) %>%
  summarise(mean_ir = mean(ir, na.rm = TRUE)) %>%
  ungroup()
```

```{r}
flow_lpm <- 1
duration_days <- 7
filter_diam_mm <- 37

a <- pi * ((filter_diam_mm - 2)/(2 * 1000))^2   # m^2 (filter effective area)
q <- flow_lpm / (60 * 1000)                      # m^3/s (1 L/min)
dt <- duration_days * 24 * 60 * 60                # s (7 days)
rho_atn <- 12.5                              # m^2/g
```

```{r}
d_bc <- tibble(max = max(df_clean$mean_ir),
               min = min(df_clean$mean_ir),
               d_atn = 100 * log(max/min),
               b_atn = (a * d_atn) / (q * dt),
               vol = q * dt,
               r = exp(-d_atn / 100) * 0.88 + 0.12,
               bc_conc = 1e4 * b_atn / (rho_atn * r))
```


For a `r duration_days` day sample, at `r flow_lpm` L/min, onto a `r filter_diam_mm` filter, repeated on `r length(unique(df_clean$date))` days, the effective blank-to-blank variabilty in BC is `r round(d_bc$bc_conc[1], 1)` $\mu g/m^{-3}$, based on the maximum and minimum IR transmission. 
